---
title: "API Doc"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{API Doc}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r, include = FALSE}
library(flaiR)
library(reticulate)
# system(paste(reticulate::py_config()$python, "-m pip install flair"))
# reticulate::py_install("flair")
```

## flair

```{r}
flair <- import_flair()
```


### flair$.cache_root = PosixPath('/home/runner/.flair')

<div style="text-align: justify">

```r
flair$cache_root = PosixPath('/home/runner/.flair')
```
The path to the cache folder Flair is using.

This value defaults to <Home Directory>/.flair. You can choose the path by setting the FLAIR_CACHE_ROOT environment variable.

</div>


### flair$device: device = device(type='cpu')


<div style="text-align: justify">

```{r}
flair$device
```


Flair is using a single device for everything. You can set this device by overwriting this variable.

This value will be automatically set to the first found GPU if available and to CPU otherwise. You can choose a specific GPU, by setting the FLAIR_DEVICE environment variable to its index.

</div>

### flair$logger = <Logger flair (INFO)> 


<div style="text-align: justify">

```{r}
flair$logger
```

The logger used by Flair.

You can reconfigure it to change the log output to your likings.

</div>

###  flair$set_seed(seed) [View on](https://github.com/flairNLP/flair/blob/v0.13.0/flair/__init__.py#L74-L83)  




```{r}
flair$set_seed(2024L)
```

Set the seed for all random generators used in training.

Use this method to guarantee reproducibility of experiments.

</div>


> Parameters:
>>  seed (int) – In the R programming language, appending L to a number explicitly designates that number as an integer. When you add L to a number, you're instructing R to treat this number as an integer rather than a double-precision floating-point number.




## flair_data

```{r}
flair_data <- flair_data()
```



