---
title: "Tagging Sentiment with Flair Standard Models"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tagging Sentiment with Flair Standard Models}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r include=FALSE}
# reticulate::use_condaenv("r-reticulate")
reticulate::py_install("flair")
```

## List of Sentiment Models
| ID                      | Language | Task                                                      | Training Dataset           | Accuracy           |
|-------------------------|----------|-----------------------------------------------------------|----------------------------|--------------------|
| 'sentiment'             | English  | detecting positive and negative sentiment (transformer-based) | movie and product reviews | 98.87              |
| 'sentiment-fast'        | English  | detecting positive and negative sentiment (RNN-based)     | movie and product reviews | 96.83              |
| 'de-offensive-language' | German   | detecting offensive language                              | GermEval 2018 Task 1       | 75.71 (Macro F1)   |

__Source__: https://flairnlp.github.io/docs/tutorial-basics/tagging-sentiment


## An Example Using `sentiment` Model (Pre-trained English Model)


```{r}
library(flaiR)
library(reticulate)
```


```{r create-dataset}
texts <- c("UCD is one of the best universities in Ireland.",
           "UCD has a good campus but is very far from my apartment in Dublin.",
           "Essex is famous for social science research.",
           "Essex is not in the Russell Group, but it is famous for political science research and in 1994 Group.",
           "TCD is the oldest university in Ireland.",
           "TCD is similar to Oxford.")
doc_ids <- c("doc1", "doc2", "doc3", "doc4", "doc5", "doc6")
```


```{r setup}
library(flaiR)
tagger_sent <- load_tagger_sentiments("sentiment")
results <- get_sentiments(texts, doc_ids, tagger_sent)
head(results, n = 10)
```

