---
title: "Tagging Sentiment with Flair Standard Models"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tagging Sentiment with Flair Standard Models}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r include=FALSE}
reticulate::py_install("flair")
```

## List of Sentiment Models
| ID                      | Language | Task                                                      | Training Dataset           | Accuracy           |
|-------------------------|----------|-----------------------------------------------------------|----------------------------|--------------------|
| 'sentiment'             | English  | detecting positive and negative sentiment (transformer-based) | movie and product reviews | 98.87              |
| 'sentiment-fast'        | English  | detecting positive and negative sentiment (RNN-based)     | movie and product reviews | 96.83              |
| 'de-offensive-language' | German   | detecting offensive language                              | GermEval 2018 Task 1       | 75.71 (Macro F1)   |

__Source__: https://flairnlp.github.io/docs/tutorial-basics/tagging-sentiment


## An Example Using `sentiment` Model (Pre-trained English Model)


```{r}
library(flaiR)
data("uk_immigration")
uk_immigration <- head(uk_immigration, 5)
```

Download the English sentiment model from FlairNLP on Hugging Face. Currently, it also supports a large English sentiment model and a German pre-trained model.
```{r}
tagger_sent <- load_tagger_sentiments("sentiment")
```



```{r setup}
results <- get_sentiments(uk_immigration$text, seq_len(nrow(uk_immigration)), tagger_sent)

print(results)
```



