---
title: "Tagging Sentiment with Flair Standard Models"
author: 
  - name: "David (Yen-Chieh) Liao"
    affiliation: "Postdoc at Text & Policy Research Group and SPIRe in UCD"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tagging Sentiment with Flair Standard Models}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, include = FALSE}
library(flaiR)
library(reticulate)

# system(paste(reticulate::py_config()$python, "-m pip install flair"))
reticulate::py_install("flair")

```


## An Example Using `sentiment` Model (Pre-trained English Model)
```{r}
library(flaiR)
data("uk_immigration")
uk_immigration <- head(uk_immigration, 5)
```

<div style="text-align: justify">

Download the English sentiment model from FlairNLP on [Hugging Face](https://huggingface.co/flair). Currently, it also supports a large English sentiment model and a German pre-trained model.

```{r}
tagger_sent <- load_tagger_sentiments("sentiment")
```

Flair NLP operates under the [PyTorch](https://pytorch.org) framework. As such, we can use the `$to` method to set the device for the Flair Python library. The flair_device("cpu")  allows you to select whether to use the CPU, CUDA devices (like cuda:0, cuda:1, cuda:2), or specific MPS devices on Mac (such as mps:0, mps:1, mps:2). For information on Accelerated PyTorch training on Mac, please refer to https://developer.apple.com/metal/pytorch/. For more about CUDA, please visit: https://developer.nvidia.com/cuda-zone 

```{r eval=FALSE, include=TRUE}
tagger_sent$to(flair_device("mps")) 
```

```
TextClassifier(
  (embeddings): TransformerDocumentEmbeddings(
    (model): DistilBertModel(
      (embeddings): Embeddings(
        (word_embeddings): Embedding(30522, 768, padding_idx=0)
        (position_embeddings): Embedding(512, 768)
        (LayerNorm): LayerNorm((768,), eps=1e-12, elementwise_affine=True)
        (dropout): Dropout(p=0.1, inplace=False)
      )
      (transformer): Transformer(
        (layer): ModuleList(
          (0-5): 6 x TransformerBlock(
            (attention): MultiHeadSelfAttention(
              (dropout): Dropout(p=0.1, inplace=False)
              (q_lin): Linear(in_features=768, out_features=768, bias=True)
              (k_lin): Linear(in_features=768, out_features=768, bias=True)
              (v_lin): Linear(in_features=768, out_features=768, bias=True)
              (out_lin): Linear(in_features=768, out_features=768, bias=True)
            )
            (sa_layer_norm): LayerNorm((768,), eps=1e-12, elementwise_affine=True)
            (ffn): FFN(
              (dropout): Dropout(p=0.1, inplace=False)
              (lin1): Linear(in_features=768, out_features=3072, bias=True)
              (lin2): Linear(in_features=3072, out_features=768, bias=True)
              (activation): GELUActivation()
            )
            (output_layer_norm): LayerNorm((768,), eps=1e-12, elementwise_affine=True)
          )
        )
      )
    )
  )
  (decoder): Linear(in_features=768, out_features=2, bias=True)
  (dropout): Dropout(p=0.0, inplace=False)
  (locked_dropout): LockedDropout(p=0.0)
  (word_dropout): WordDropout(p=0.0)
  (loss_function): CrossEntropyLoss()
)
```
```{r }
results <- get_sentiments(uk_immigration$text, seq_len(nrow(uk_immigration)),
                          tagger_sent)
```

```{r}
print(results)
```

</div>

## Batch Processing in English Sentiment Model
<div style="text-align: justify">

Processing texts individually can be both inefficient and memory-intensive. On the other hand, processing all the texts simultaneously could surpass memory constraints, especially if each document in the dataset is sizable. Parsing the documents in smaller batches may provide an optimal compromise between these two scenarios. Batch processing can enhance efficiency and aid in memory management.

By default, the batch_size parameter is set to 5. You can consider starting with this default value and then experimenting with different batch sizes to find the one that works best for your specific use case. You can monitor memory usage and processing time to help you make a decision. If you have access to a GPU, you might also try larger batch sizes to take advantage of GPU parallelism. However, be cautious not to set the batch size too large, as it can lead to out-of-memory errors. Ultimately, the choice of batch size should be based on a balance between memory constraints, processing efficiency, and the specific requirements of your entity extraction task.

</div>
```{r}
batch_process_results  <- get_sentiments_batch(uk_immigration$text,
                                               uk_immigration$speaker, 
                                               tagger_sent, 
                                               show.text_id = FALSE,
                                               batch_size = 2,
                                               verbose = TRUE)
```

```{r}
print(batch_process_results)
```

