---
title: "Tagging Part-of-Speech Tagging with Flair Standard Models"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tagging Part-of-Speech Tagging with Flair Standard Models}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r include=FALSE}
reticulate::py_install("flair")
```

## List of Part-of-Speech Tagging Models

| ID              | Task                     | Language            | Training Dataset                  | Accuracy             | Contributor / Notes                 |
|-----------------|--------------------------|---------------------|-----------------------------------|----------------------|-------------------------------------|
| 'pos'           | POS-tagging              | English             | Ontonotes                         | 98.19 (Accuracy)     |                                     |
| 'pos-fast'      | POS-tagging              | English             | Ontonotes                         | 98.1 (Accuracy)      | (fast model)                        |
| 'upos'          | POS-tagging (universal)  | English             | Ontonotes                         | 98.6 (Accuracy)      |                                     |
| 'upos-fast'     | POS-tagging (universal)  | English             | Ontonotes                         | 98.47 (Accuracy)     | (fast model)                        |
| 'pos-multi'     | POS-tagging              | Multilingual        | UD Treebanks                      | 96.41 (average acc.) | (12 languages)                      |
| 'pos-multi-fast'| POS-tagging              | Multilingual        | UD Treebanks                      | 92.88 (average acc.) | (12 languages)                      |
| 'ar-pos'        | POS-tagging              | Arabic (+dialects)  | combination of corpora            |                      |                                     |
| 'de-pos'        | POS-tagging              | German              | UD German - HDT                   | 98.50 (Accuracy)     |                                     |
| 'de-pos-tweets' | POS-tagging              | German              | German Tweets                     | 93.06 (Accuracy)     | stefan-it                           |
| 'da-pos'        | POS-tagging              | Danish              | Danish Dependency Treebank        |                      | AmaliePauli                         |
| 'ml-pos'        | POS-tagging              | Malayalam           | 30000 Malayalam sentences        | 83                   | sabiqueqb                           |
| 'ml-upos'       | POS-tagging              | Malayalam           | 30000 Malayalam sentences        | 87                   | sabiqueqb                           |
| 'pt-pos-clinical'|POS-tagging              | Portuguese          | PUCPR                             | 92.39                | LucasFerroHAILab for clinical texts|
| 'pos-ukrainian' | POS-tagging              | Ukrainian           | Ukrainian UD                      | 97.93 (F1)           | dchaplinsky                         |

__Source__: https://flairnlp.github.io/docs/tutorial-basics/part-of-speech-tagging


## An Example Using `pos-fast` Part-of-Speech Tagging

```{r create-dataset}
texts <- c("UCD is one of the best universities in Ireland.",
           "UCD has a good campus but is very far from my apartment in Dublin.",
           "Essex is famous for social science research.",
           "Essex is not in the Russell Group, but it is famous for political science research and in 1994 Group.",
           "TCD is the oldest university in Ireland.",
           "TCD is similar to Oxford.")
doc_ids <- c("doc1", "doc2", "doc3", "doc4", "doc5", "doc6")
```


```{r}
library(flaiR)
tagger_pos <- flaiR::load_tagger_pos("pos-fast")
results <- get_pos(texts, doc_ids, tagger_pos)
head(results, n = 10)
```

