---
title: "Tagging Part-of-Speech Tagging with Flair Standard Models"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tagging Part-of-Speech Tagging with Flair Standard Models}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r include=FALSE}
reticulate::py_install("flair")
```

## List of Part-of-Speech Tagging Models

| ID              | Task                     | Language            | Training Dataset                  | Accuracy             | Contributor / Notes                 |
|-----------------|--------------------------|---------------------|-----------------------------------|----------------------|-------------------------------------|
| 'pos'           | POS-tagging              | English             | Ontonotes                         | 98.19 (Accuracy)     |                                     |
| 'pos-fast'      | POS-tagging              | English             | Ontonotes                         | 98.1 (Accuracy)      | (fast model)                        |
| 'upos'          | POS-tagging (universal)  | English             | Ontonotes                         | 98.6 (Accuracy)      |                                     |
| 'upos-fast'     | POS-tagging (universal)  | English             | Ontonotes                         | 98.47 (Accuracy)     | (fast model)                        |
| 'pos-multi'     | POS-tagging              | Multilingual        | UD Treebanks                      | 96.41 (average acc.) | (12 languages)                      |
| 'pos-multi-fast'| POS-tagging              | Multilingual        | UD Treebanks                      | 92.88 (average acc.) | (12 languages)                      |
| 'ar-pos'        | POS-tagging              | Arabic (+dialects)  | combination of corpora            |                      |                                     |
| 'de-pos'        | POS-tagging              | German              | UD German - HDT                   | 98.50 (Accuracy)     |                                     |
| 'de-pos-tweets' | POS-tagging              | German              | German Tweets                     | 93.06 (Accuracy)     | stefan-it                           |
| 'da-pos'        | POS-tagging              | Danish              | Danish Dependency Treebank        |                      | AmaliePauli                         |
| 'ml-pos'        | POS-tagging              | Malayalam           | 30000 Malayalam sentences        | 83                   | sabiqueqb                           |
| 'ml-upos'       | POS-tagging              | Malayalam           | 30000 Malayalam sentences        | 87                   | sabiqueqb                           |
| 'pt-pos-clinical'|POS-tagging              | Portuguese          | PUCPR                             | 92.39                | LucasFerroHAILab for clinical texts|
| 'pos-ukrainian' | POS-tagging              | Ukrainian           | Ukrainian UD                      | 97.93 (F1)           | dchaplinsky                         |

__Source__: https://flairnlp.github.io/docs/tutorial-basics/part-of-speech-tagging


## An Example Using `pos-fast` Part-of-Speech Tagging

```{r}
library(flaiR)
data("de_immigration")
```

```{r}
tagger_pos <- load_tagger_pos("pos")
de_immigration <- head(de_immigration, 4)
results <- get_pos(de_immigration$text, de_immigration$speaker, tagger_pos)
head(results, n = 10)
```

