---
title: "Quick Start"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick Start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r include=FALSE}
flaiR::clear_flair_cache()
reticulate::use_condaenv(reticulate::py_config()[[1]])
```

## Get Started with Using [`remotes`](https://github.com/r-lib/remotes):

<div style="text-align: justify">


To utilize flairR in R, you need to first install the Python-based Flair NLP library. This can be done using reticulate. It's recommended to have Python version 3.7 or higher installed to ensure smooth operation of [`fliar`](https://flairnlp.github.io) in Python. The functionality of flairR is primarily limited to the pre-trained models provided by [`fliar`](https://flairnlp.github.io). The `flairR` returns the tagging information directly in a data.table format. Note that using the transformed base NLP toolkit can be computationally intensive. Therefore, implementing parallel computing is advised to enhance the performance of NLP tasks.

</div>

-----

## Quick Use

### Tagging Parts-of-Speech with Flair Models
Load the pretrained model "pos-fast". For more pretrained models, see https://flairnlp.github.io/docs/tutorial-basics/part-of-speech-tagging#-in-english.

```{r}
library(reticulate)
library(data.table)
library(flaiR)
texts <- c("UCD is one of the best universities in Ireland.",
           "UCD has a good campus but is very far from my apartment in Dublin.",
           "Essex is famous for social science research.",
           "Essex is not in the Russell Group, but it is famous for political science research and in 1994 Group.",
           "TCD is the oldest university in Ireland.",
           "TCD is similar to Oxford.")

doc_ids <- c("doc1", "doc2", "doc3", "doc4", "doc5", "doc6")
tagger_pos = import("flair.nn")$Classifier$load('pos-fast')
results <- get_pos(texts, doc_ids, tagger_pos)
head(results, n = 10)
```


### Tagging Entities with Flair Models

Load the pretrained model "ner". For more pretrained models, see https://flairnlp.github.io/docs/tutorial-basics/tagging-entities.

```{r}
library(reticulate)
library(data.table)
tagger_ner = import("flair.nn")$Classifier$load('ner')
results <- get_entities(texts, doc_ids, tagger_ner)
head(results, n = 10)
```



### __Tagging Sentiment__ 

Load the pretrained model "`sentiment`".  The pre-trained models of "`sentiment`", "`sentiment-fast`", and "`de-offensive-language`" are currently available. For more pretrained models, see https://flairnlp.github.io/docs/tutorial-basics/tagging-sentiment.

```{r}
library(reticulate)
library(data.table)
tagger_sent = import("flair.nn")$Classifier$load('sentiment')
results <- get_sentiments(texts, doc_ids, tagger_sent)
head(results, n = 10)
```

-----

## __How to Contribute__

<div style="text-align: justify">

Contributions in the form of comments, code suggestions, and tutorial examples are very welcome. Please note that the `flaiR` is released with the [Contributor Code of Conduct](https://github.com/davidycliao/flaiR/blob/master/CONDUCT.md). By contributing to this project, you agree to abide by its terms.

</div>

