---
title: "Quick Start"
# author: 
#   - name: "David (Yen-Chieh) Liao"
#     affiliation: "Postdoc at Text & Policy Research Group and SPIRe in UCD"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick Start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r include=FALSE}
# library(reticulate)
# library(flaiR)
# # reticulate::py_install("flair")
# system(paste(reticulate::py_config()$python, "-m pip install flair"))
# system(paste(Sys.which("python3"), "-m pip install --upgrade pip"))
# system(paste(Sys.which("python3"), "-m pip install torch"))
# system(paste(Sys.which("python3"), "-m pip install flair"))
# Sys.setenv(RETICULATE_PYTHON = Sys.which("python3"))
library(flaiR)
```


<div style="text-align: justify">

Flair is a Python library developed by [Zalando Research](https://engineering.zalando.com/posts/2018/11/zalando-research-releases-flair.html) that stands out as a notably user-friendly NLP framework. Flair NLP provides intuitive interfaces with exceptional multilingual embeddings, especially for various multilingual embedding frameworks like GloVe and transformer-based models on Hugging Face.

</div>


# flaiR Installation

__System Requirements:__

- Python >= 3.9
- R >= 4.2.0
- Rstudio

## Option 1: Fast Install Python with `reticulate` and 

1. Install Python automatically through R reticulate:
```
# Install and load reticulate package
install.packages("reticulate")
library(reticulate)
```

2. Install Python 3.10 using reticulate:
```
install_python(version = "3.10")
```

3. Verify the Python installation and see which version is being used:
```
py_config()  # Shows Python configuration details
```

4. To install flaiR package:
```
install.packages("remotes")
remotes::install_github("davidycliao/flaiR", force = TRUE)
```

5. Load the flaiR package (when the message is printed showing the corresponding flair NLP python version, it indicates successful attachment of Flair NLP python to your R):
```
library(flaiR)
```

```
#> flaiR: An R Wrapper for Accessing Flair NLP 0.13.1
```

## Option 2: Docker Setup 

The Docker image (12.5GB) includes a complete R/Python development environment with RStudio Server + R environments and Python 3.9 with flair NLP and its dependencies (PyTorch, models).

Please ensure your system meets these requirements:

- At least 15GB of free disk space
- Minimum 16GB RAM recommended
- Stable internet connection for initial download
- Docker installed and running

__Intel/AMD Processors:__

```bash
# Pull and run
docker pull ghcr.io/davidycliao/flair-rstudio:latest
docker run -d \
  -p 8787:8787 \
  --user root \
  -e USER=rstudio \
  -e PASSWORD=rstudio123 \
  --name flair-rstudio \
  ghcr.io/davidycliao/flair-rstudio:latest
```

__Apple Silicon (M1 Series MacOS):__


```bash
# Pull and run with platform specification
docker pull --platform linux/amd64 ghcr.io/davidycliao/flair-rstudio:latest
docker run -d \
  -p 8787:8787 \
  --platform linux/amd64 \
  --user root \
  -e USER=rstudio \         
  -e PASSWORD=rstudio123 \
  --name flair-rstudio \
  ghcr.io/davidycliao/flair-rstudio:latest
```

__Access RStudio Server:__

- Open browser: [`http://localhost:8787`](http://localhost:8787)
- Username: `rstudio`
- Password: `rstudio123`


## Troubleshooting Guide 

The `faiR` Will:

- Automatically check Python environment
- Install required Python packages (flair and its dependencies)
- Configure the Python-R connection

```r
install.packages("remotes")
remotes::install_github("davidycliao/flaiR", force = TRUE)
```

<div style="text-align: justify">

Installation typically proceeds automatically with RStudio and R handling dependencies. However, users (particularly those with Mac ARM64 systems) may encounter compilation issues. Here's a comprehensive guide to resolve common problems:


###  __Mac M1/M2 (Apple Silicon) Specific Setup__

1 Architecture Options

  - Requires specific compiler setup
  - May encounter additional compatibility issues

2. Native ARM64 Version

  - Requires specific compiler setup
  - May encounter additional compatibility issues

###   __Compiler Setup for ARM64 Systems__

Required Steps:

1. Download GNU Fortran from `https://mac.r-project.org/tools/`

2. For R 4.3.0+:
  - Install GNU Fortran 12.2 (universal)
  - Supports both Intel and Apple Silicon
  - Download `gfortran-12.2-universal.pkg` (242MB) from:
    + [CRAN macOS tools page](CRAN macOS tools page)
    + [GitHub R-macos GNU Fortran releases](https://github.com/fxcoudert/gfortran-for-macOS/releases)
</div>

### __Automatic Dependencies (Python)__

<div style="text-align: justify">


`flaiR` R package will automatically install the following Python packages during setup:

__Core Dependencies__
- Python (3.9 or 3.10 recommended)
- flair[word-embeddings] (>=0.11.3)
- numpy (>=1.22.4, <1.29.0)
- PyTorch (>=2.0.0, <2.6.0)
- scipy (==1.12.0)

__Additional Dependencies__
- gensim (>=4.3.2)
- transformers (>=4.30.0)
- sentencepiece (>=0.1.99)
- bpemb (>=0.3.5)


All other required dependencies will be automatically handled during the installation process.
You can manage Python settings in RStudio through `Tools -> Global Options -> Python`.

To check your Python configuration, use:


</div>

```r
reticulate::py_config()
```

### __Recommended Configurations__

For stable usage, we strongly recommend installing these specific versions.

| OS      | R Versions                 | Python Version |
|---------|----------------------------|----------------|
| Mac     | 4.3.2, 4.2.0, ~~4.2.1~~*   | 3.10.x, 3.9    |
| Windows | 4.0.5, Latest              | 3.10.x, 3.9    |
| Ubuntu  | 4.3.2, 4.2.0, 4.2.1        | 3.10.x, 3.9    |


### __R Version Requirements__

The flaiR package has specific R version requirements based on Matrix package compatibility:

- R 4.5.0+: Matrix 1.7-0 or newer
- R 4.4.x: Matrix 1.6-x
- R 4.3.x: Matrix 1.5-1
- R 4.2.x: Matrix 1.4-1


*: _On R 4.2.1, particularly when using the Matrix package on ARM 64 architecture Macs (M1/M2), compatibility issues with gfortran may occur. It's recommended to avoid this combination._


&nbsp;

<div style="text-align: justify">


If you encounter any problems or have questions:

- Check the documentation
- Visit our Issues page
- Join our [Discussion forum](https://github.com/davidycliao/flaiR/discussions)

</div>


###  __Troubleshooting for Docker__

1. If you encounter any issues:

```
# Try using a different port (e.g., 8788)
docker run -d \
  -p 8788:8787 \
  --platform linux/amd64 \
  --user root \
  --name flair-rstudio \
  ghcr.io/davidycliao/flair-rstudio:latest
```
Then access via [`http://localhost:8788`](http://localhost:8788)

2. Container already exists:

```
# Remove existing container
docker stop flair-rstudio
docker rm flair-rstudio
```

Then retry the run command.

3. Check container status:

```
# View running containers
docker ps
# View all containers including stopped ones
docker ps -a
# View container logs
docker logs flair-rstudio
```










-----

## NLP Tasks


<div style="text-align: justify">

For R users, flairR extends FlairNLP with three NLP task functions to extract features in a neat format with [data.table](https://cran.r-project.org/web/packages/data.table/index.html). Through these featured functions, you don't have to write loops to format parsed output on your own. The main features include part-of-speech tagging, named entity recognition and sentiment analysis. Additionally, to handle the load on RAM when dealing with larger corpora, flairR supports batch processing to handle texts in batches, which is especially useful when dealing with large datasets, to optimize memory usage and performance.

| **Core  Featured Functions**    | Loader                     | Supported Models from Flair NLP  |
|---------------------------------|----------------------------|----------------------------------|
| `get_entities()`                | `load_tagger_ner()`        | `en` (English), `fr` (French), `da` (Danish), `nl` (Dutch), and more.                                                    |
| `get_pos()`                     | `load_tagger_pos()`        | `pos` (English POS), `fr-pos` (French POS), `de-pos` (German POS), `nl-pos` (Dutch POS), and more.                       |

</div>

&nbsp;


## Training and Fine-tuning

<div style="text-align: justify">

In __flairR__, we use the simplest __S3__ method to wrap major modules. All modules will work like [R6](https://bookdown.dongzhuoer.com/hadley/adv-r/s3-r6) in the R environment when loaded from Flair NLP. In Python, both functions and methods (sometimes referred to as functions in R) within a class can be accessed using the `$` operator. For example, `from flair.trainers import ModelTrainer` in Python is equivalent to `ModelTrainer <- flair_trainers()$ModelTrainer` in  R environment with __flairR__.

</div>

| **Wrapped Flair NLP Modules with S3**             | Corresponding Code Practices When Loading Modules from FlairNLP  | 
|---------------------------------------------------|------------------------------------------------------------------|
| `flair_datasets()`                                | from flair.datasets import *                                     |
| `flair_nn()`                                      | from flair.nn import *                                           |
| `flair_splitter()`                                | from flair.splitter import *                                     |
| `flair_trainers()`                                | from flair.trainers import *                                     |
| `flair_models()`                                  | from flair.models import *                                       |
 

&nbsp;

-----


