---
title: "Quick Start"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick Start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r include=FALSE}
library(reticulate)
library(flaiR)
reticulate::py_install("flair")
system(paste(reticulate::py_config()$python, "-m pip install flair"))
```

## Install `flaiR` with Using [`remotes`](https://github.com/r-lib/remotes)

<div style="text-align: justify">

`flaiR` is built on top of the reticulate package and incorporates key functions to access the core features of __FlairNLP__, returning data in a tidy and clean [`data.table`](https://cran.r-project.org/web/packages/data.table/index.html). The installation consists of two parts: First, install [Python 3.7](https://www.python.org/downloads/) or higher. ~~Additionally, you'll also need [`Anaconda`](Anaconda) to assist `reticulate` in setting up your Python environment, as well as enabling your RStudio to identify the environment.~~

__System Requirement:__

- Python (>= 3.7.0)

- R (>= 3.6.3)

- Anaconda ___(optional)___

```
install.packages("remotes")
remotes::install_github("davidycliao/flaiR", force = TRUE)
library(flaiR)
```
```
 flaiR: An R Wrapper for Accessing Flair NLP Tagging Features      
 Python : 3.11  
```


If you're using Python-based packages in R for the first time, such as {`flaiR`} or {`reticulate`}, you probably haven't installed a Conda environment yet. When loading flaiR in R, two main steps occur. First, __a Conda environment is created through {`reticulate`}__. During this process, you will observe numerous messages related to the installation of the Python environment and the Python flair module. Notably, flair has numerous dependencies, including libraries related to transformers (like the Hugging Face API). Thus, the installation might take some time to complete.

Afterward, you will see the message __"Virtual environment 'r-reticulate' successfully created."__ Next, you will be prompted to confirm whether or not you want to use `r-reticulate`. Enter __"Yes,"__ and it will automatically install `flair` via your conda environment in Python.  If there are any issues with the installation, feel free to ask in the <u>[Discussion](https://github.com/davidycliao/flaiR/discussions)</u>.

###### ___Note___: It's worth noting that using transformer-based pre-trained models from FlairNLP can be computationally intensive. Therefore, it's recommended to implement parallel computing to enhance the performance and efficiency of the tasks.




&nbsp;


</div>

-----

## User Guaide 

### __Tagging Parts-of-Speech with Flair Models__

<div style="text-align: justify">

You can load the pre-trained model `"pos-fast"`. For more pre-trained models, see https://flairnlp.github.io/docs/tutorial-basics/part-of-speech-tagging#-in-english.

</div>

```{r}
texts <- c("UCD is one of the best universities in Ireland.",
           "UCD has a good campus but is very far from my apartment in Dublin.",
           "Essex is famous for social science research.",
           "Essex is not in the Russell Group, but it is famous for political science research and in 1994 Group.",
           "TCD is the oldest university in Ireland.",
           "TCD is similar to Oxford.")

doc_ids <- c("doc1", "doc2", "doc3", "doc4", "doc5", "doc6")
```

```{r}
library(flaiR)
```

```{r}
tagger_pos <- load_tagger_pos("pos-fast")
```

```{r}
results <- get_pos(texts, doc_ids, tagger_pos)
head(results, n = 10)
```


### __Tagging Entities with Flair Models__

<div style="text-align: justify">

Load the pretrained model "ner". For more pretrained models, see https://flairnlp.github.io/docs/tutorial-basics/tagging-entities.

</div>

```{r}
library(flaiR)
```

```{r}
tagger_ner <- load_tagger_ner("ner")
```

```{r}
results <- get_entities(texts, doc_ids, tagger_ner)
head(results, n = 10)
```

### __Tagging Sentiment__

<div style="text-align: justify">
Load the pretrained model "`sentiment`". The pre-trained models of "`sentiment`", "`sentiment-fast`", and "`de-offensive-language`" are currently available. For more pretrained models, see https://flairnlp.github.io/docs/tutorial-basics/tagging-sentiment.

</div>

```{r}
library(flaiR)
```

```{r}
tagger_sent <- load_tagger_sentiments("sentiment")
```


```{r}
results <- get_sentiments(texts, doc_ids, tagger_sent)
head(results, n = 10)
```

&nbsp;

-----


## How to Contribute

<div style="text-align: justify">

Contributions in the form of comments, code suggestions, and tutorial examples are very welcome. Please note that the `flaiR` is released with the [Contributor Code of Conduct](https://github.com/davidycliao/flaiR/blob/master/CONDUCT.md). By contributing to this project, you agree to abide by its terms.

</div>




