---
title: "Quick Start"
# author: 
#   - name: "David (Yen-Chieh) Liao"
#     affiliation: "Postdoc at Text & Policy Research Group and SPIRe in UCD"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick Start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r include=FALSE}
# library(reticulate)
# library(flaiR)
# # reticulate::py_install("flair")
# system(paste(reticulate::py_config()$python, "-m pip install flair"))
system(paste(Sys.which("python3"), "-m pip install --upgrade pip"))
system(paste(Sys.which("python3"), "-m pip install torch"))
system(paste(Sys.which("python3"), "-m pip install flair"))
Sys.setenv(RETICULATE_PYTHON = Sys.which("python3"))
library(flaiR)
```


<div style="text-align: justify">

Flair is a Python library developed by [Zalando Research](https://engineering.zalando.com/posts/2018/11/zalando-research-releases-flair.html) that stands out as a notably user-friendly NLP framework. Flair NLP provides intuitive interfaces with exceptional multilingual embeddings, especially for various multilingual embedding frameworks like GloVe and transformer-based models on Hugging Face.

</div>


## flaiR Installation

## Option 1: Direct Installation

__System Requirements:__

- Python >= 3.10
- R >= 4.2.0
- Rstudio

#### macOS Terminal

```bash
# Install Python 3.10 or higher.
brew install python@3.10

# Verify Python installation
python3 --version

# Install R
brew install R

# Verify R installation
R --version

# Install RStudio
brew install --cask rstudio
```

#### PowerShell for Windows

```bash
# Download Python installer from python.org and run:
# https://www.python.org/downloads/

# Verify Python installation
python --version

# Install R
# Download R installer from CRAN and run:
# https://cran.r-project.org/bin/windows/base/

# Verify R installation
R --version
```

## Option 2: Docker Setup 

The Docker image (12.5GB) includes a complete R/Python development environment with RStudio Server + R environments and Python 3.9 with flair NLP and its dependencies (PyTorch, models).

Please ensure your system meets these requirements:

- At least 15GB of free disk space
- Minimum 16GB RAM recommended
- Stable internet connection for initial download
- Docker installed and running

__Intel/AMD Processors:__

```bash
# Pull and run
docker pull ghcr.io/davidycliao/flair-rstudio:latest
docker run -p 8787:8787 ghcr.io/davidycliao/flair-rstudio:latest
```

- Apple Silicon (M1/M2 Mac):

```bash
# Pull and run with platform specification
docker pull --platform linux/amd64 ghcr.io/davidycliao/flair-rstudio:latest
docker run --platform linux/amd64 -p 8787:8787 ghcr.io/davidycliao/flair-rstudio:latest
```

__Access RStudio Server:__

- Open browser: `http://localhost:8787`
- Username: `rstudio`
- Password: `rstudio123`


### R Package Installation

The `faiR` Will:

- Automatically check Python environment
- Install required Python packages (flair and its dependencies)
- Configure the Python-R connection

```r
install.packages("remotes")
remotes::install_github("davidycliao/flaiR", force = TRUE)
```

#### Notice:

<div style="text-align: justify">
Installation should work automatically as RStudio and R handle the dependencies.  However, users may encounter compilation errors, particularly with the Matrix package on Mac ARM64 systems (M1/M2 chips). These issues often stem from version conflicts between the Matrix package and the gfortran compiler. To resolve these, follow these steps:

<u>**Version Compatibility:**</u> 


First, verify your R version compatibility. For Mac M1/M2 systems, ensure your R version aligns with these Matrix package dependencies:

- R 4.5.0+: Latest Matrix package version (1.7-0 or newer)
- R 4.4.x: Matrix 1.6-x
- R 4.3.x: Matrix 1.5-1
- R 4.2.x: Matrix 1.4-1

<u>**Architecture Compatibility:**</u> 

- Ensure you've downloaded the correct R version for your Mac's processor architecture (Apple Silicon or Intel).
- For Apple M1/M2 systems, consider using the official Intel 64-bit R version running through Rosetta, rather than the native arm64 version.

<u>**Compiler Issues:**</u> 

- For arm64 systems, you may need to download and install GNU Fortran from https://mac.r-project.org/tools/.
- For R 4.3.0 and above, you'll need GNU Fortran 12.2 (universal) compiler, which supports both Intel and Apple Silicon architectures. macOS users should download and install gfortran-12.2-universal.pkg (242MB) from either the CRAN macOS tools page or GitHub R-macos GNU Fortran releases. This is a significant change from earlier versions (R 3.5.0-3.6.3) which used GNU Fortran 6.1, and ensures proper compilation of the Matrix package on modern Mac systems.


However, if you encounter Matrix package compilation errors (which commonly occur on Mac ARM64 systems due to version conflicts between the Matrix package and the gfortran compiler), you'll need to verify your R version compatibility first.
For Mac M1/M2 systems, ensure your R version matches these Matrix package dependencies:


<!-- ```bash -->
<!-- brew install gcc -->
<!-- ``` -->
<!-- - Configure R compiler settings: -->

<!-- ```bash -->
<!-- mkdir -p ~/.R -->
<!-- touch ~/.R/Makevars -->
<!-- echo "FC=$(brew --prefix)/bin/gfortran" >> ~/.R/Makevars -->
<!-- echo "F77=$(brew --prefix)/bin/gfortran" >> ~/.R/Makevars -->
<!-- echo "FLIBS=-L$(brew --prefix)/lib/gcc/current -lgfortran -lquadmath -lm" >> ~/.R/Makevars -->
```

#### Python Dependencies

<div style="text-align: justify">

The following Python packages will be installed automatically by flaiR:

- flair
- scipy==1.12.0
- gensim==4.3.2

`flaiR` will automatically detect and configure your Python environment:

1. Checks for Python 3.10 or higher
2. Installs required Python packages
3. Configures R-Python interface using reticulate

Note: You can manage Python settings in RStudio through _Tools -> Global Options -> Python_. To check your Python configuration, use:

</div>

```r
reticulate::py_config()
```

#### Recommended Configurations

For stable usage, we strongly recommend installing these specific versions.

| OS      | R Versions                 | Python Version |
|---------|----------------------------|----------------|
| Mac     | 4.3.2, 4.2.0, ~~4.2.1~~*   | 3.10.x, 3.9    |
| Windows | 4.0.5, Latest              | 3.10.x, 3.9    |
| Ubuntu  | 4.3.2, 4.2.0, 4.2.1        | 3.10.x, 3.9    |

*: _On R 4.2.1, particularly when using the Matrix package on ARM 64 architecture Macs (M1/M2), compatibility issues with gfortran may occur. It's recommended to avoid this combination._



#### Troubleshooting

<div style="text-align: justify">


If you encounter any problems or have questions:

- Check the documentation
- Visit our Issues page
- Join our [Discussion forum](https://github.com/davidycliao/flaiR/discussions)

</div>


&nbsp;

-----

## NLP Tasks

<div style="text-align: justify">

For R users, flairR extends FlairNLP with three NLP task functions to extract features in a neat format with [data.table](https://cran.r-project.org/web/packages/data.table/index.html). Through these featured functions, you don't have to write loops to format parsed output on your own. The main features include part-of-speech tagging, named entity recognition and sentiment analysis. Additionally, to handle the load on RAM when dealing with larger corpora, flairR supports batch processing to handle texts in batches, which is especially useful when dealing with large datasets, to optimize memory usage and performance.

| **Core  Featured Functions**    | Loader                     | Supported Models from Flair NLP  |
|---------------------------------|----------------------------|----------------------------------|
| `get_entities()`                | `load_tagger_ner()`        | `en` (English), `fr` (French), `da` (Danish), `nl` (Dutch), and more.                                                    |
| `get_pos()`                     | `load_tagger_pos()`        | `pos` (English POS), `fr-pos` (French POS), `de-pos` (German POS), `nl-pos` (Dutch POS), and more.                       |

</div>

&nbsp;


## Training and Fine-tuning

<div style="text-align: justify">

In __flairR__, we use the simplest __S3__ method to wrap major modules. All modules will work like [R6](https://bookdown.dongzhuoer.com/hadley/adv-r/s3-r6) in the R environment when loaded from Flair NLP. In Python, both functions and methods (sometimes referred to as functions in R) within a class can be accessed using the `$` operator. For example, `from flair.trainers import ModelTrainer` in Python is equivalent to `ModelTrainer <- flair_trainers()$ModelTrainer` in  R environment with __flairR__.

</div>

| **Wrapped Flair NLP Modules with S3**             | Corresponding Code Practices When Loading Modules from FlairNLP  | 
|---------------------------------------------------|------------------------------------------------------------------|
| `flair_datasets()`                                | from flair.datasets import *                                     |
| `flair_nn()`                                      | from flair.nn import *                                           |
| `flair_splitter()`                                | from flair.splitter import *                                     |
| `flair_trainers()`                                | from flair.trainers import *                                     |
| `flair_models()`                                  | from flair.models import *                                       |
 

&nbsp;

-----


