---
title: "Quick Start"
author: 
  - name: "David (Yen-Chieh) Liao"
    affiliation: "Postdoc at Text & Policy Research Group and SPIRe in UCD"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick Start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r include=FALSE}
# library(reticulate)
# library(flaiR)
# # reticulate::py_install("flair")
# system(paste(reticulate::py_config()$python, "-m pip install flair"))
system(paste(Sys.which("python3"), "-m pip install --upgrade pip"))
system(paste(Sys.which("python3"), "-m pip install torch"))
system(paste(Sys.which("python3"), "-m pip install flair"))
Sys.setenv(RETICULATE_PYTHON = Sys.which("python3"))
library(flaiR)
```


## Why Write {flaiR} to Access fair NLP in Python?
<div style="text-align: justify">

In Python, Flair ( developed by [Zalando Research](https://engineering.zalando.com/posts/2018/11/zalando-research-releases-flair.html)) stands out as a notably feature-rich and user-friendly NLP framework. Flair NLP provides intuitive interfaces with exceptional multilingual support, especially for various embedding frameworks like Glove, and transformer-based models such as BERT. 


<!-- Here are some key benefits and features of Flair that make it a valuable tool for social scientists: -->

<!-- User-Friendliness -->
<!-- Easy-to-Use API: Flair provides high-level APIs that allow users to accomplish complex NLP tasks, such as named entity recognition, sentiment analysis, and text classification, with just a few lines of code. -->
<!-- Pretrained Models -->
<!-- Pretrained Language Models: Flair leverages pretrained language models like BERT, GPT, XLNet, etc., which excel at various NLP tasks, saving users from having to train models from scratch. Researchers can also utilize advanced fine-tuning techniques created by scholars to adapt these models to specific tasks or datasets. -->
<!-- Multilingual Support -->
<!-- Multiple Languages: Social science researchers often need to handle data in multiple languages. Flair supports a wide range of languages, facilitating cross-linguistic research projects. -->
<!-- Entity Recognition and POS Tagging: These common NLP tasks in social science research help researchers to quickly extract valuable information from text. -->
<!-- For social science researchers, these features mean that they can devote more attention to the subject matter of their research, gaining access to the latest NLP techniques and deriving the data and insights they need with relative ease. -->

Flair also comes equipped with pre-trained models and context-aware capabilities. In addition, Flair also establishes dependencies with primary NLP Python libraries (such as gensim, torch, transformer, and more); installing {`flaiR`} will subsequently install other related NLP packages in Python. By installing the {`flaiR`} package in R, users can seamlessly access the Python-based Flair library within R. This integration allows for the use of basic Python libraries, like [NumPy](https://numpy.org), as well as modern NLP and deep learning frameworks such as [PyTorch](https://pytorch.org), all through the reticulate interface in an R environment.

</div>

&nbsp;

-----

## Install `flaiR` with Using [`remotes`](https://github.com/r-lib/remotes)

<div style="text-align: justify">

`flaiR` is built on top of the reticulate package and incorporates key functions to access the core features of __FlairNLP__, returning data in a tidy and clean [`data.table`](https://cran.r-project.org/web/packages/data.table/index.html). 

The installation consists of two parts: firstly, install [Python 3.8](https://www.python.org/downloads/) or above (available here; opt for the stable version, which currently goes up to 3.11, and avoid pre-release versions). Secondly, install R (version 3.6.3 or higher), along with RStudio. Additionally, you'll also need Anaconda to assist pip in safely and stably collecting dependencies for setting up your Python environment.


__System Requirement:__

- Python (>= 3.7.0)

- R (>= 3.6.3)

- RStudio 

- Anaconda ___(highly recommended)___

When first installing and loading the {flaiR} package, it utilizes the system environment tool and undergoes three evaluation stages for the automatic installation of Flair. Initially, flaiR requires at least Python 3 to be installed on your device. If Python 3 is not present, you will not be able to successfully install flaiR in R. At this point, it is essential to check if the correct version of Python is installed. We recommend installing Python 3.8 or a slightly higher version, but avoid installing pre-release versions.

Once this prerequisite is met, the installation process assesses whether the flair_env environment exists. This is to check if you are a new installer, in which case flaiR automatically creates an environment named flair_env through {reticulate}. If you already have `flair_env`, this step will be skipped when you reload {flaiR}.

In terms of installation design, we have also accounted for situations where the installation of Python might be skipped, allowing for the automatic installation of flaiR in your R environment. This typically occurs if the installation fails. After a second attempt, if the installation still fails, the user will be prompted to install 'flair' manually."

During this process, you will observe numerous messages related to the installation of the Python environment and the Python flair module. Notably, flair has numerous dependencies, including libraries related to transformers (like the Pytorch, gensim, flair, etc). Thus, the installation might take some time to complete. 

There's also another scenario to consider. If {flaiR} is unable to automatically install Flair and PyTorch, it will attempt to force the installation again. However, if this attempt fails, you'll encounter the message: "Failed to install Flair. {flaiR} requires Flair NLP. Please ensure Flair NLP is installed in Python manually." If you're using an Apple operating environment, it's essential at this point to check the compatibility of your M1/M2 chip with Python and Torch.  If there are any issues with the installation, feel free to ask in the <u>[Discussion](https://github.com/davidycliao/flaiR/discussions)</u>.


&nbsp;


When you copy the command below, you will generally be asked to upgrade the package. This is because this package operates on the {`reticulate`}, and when your packages in R are outdated, RStudio would likely display __“These packages have more recent versions available.”__ to prompt you to update. We recommend that you update.

```
install.packages("remotes")
remotes::install_github("davidycliao/flaiR", force = TRUE)
library(flaiR)
```

<!-- {`flaiR`} can be used alongside your existing Python environment on your system without the need to specifically install [Anaconda](https://github.com/conda-forge/miniforge). -->

<!-- However, we recommend using Anaconda with `flaiR`. `flaiR` can seamlessly integrate and utilize Python environments within Anaconda. This means you can leverage environments managed by Anaconda for use with `flaiR`. -->

<!-- Anaconda provides a virtual environment management tool that allows you to easily create, switch, and delete independent Python environments.  This is more flexible than using the pure Python `pip` package manager, especially when dealing with dependency issues. Additionally, Anaconda offers many pre-compiled binary packages that are typically easier to install and avoid compilation dependency problems. -->




</div>


__Installation Note__

<div style="text-align: justify">

- 20 Oct 2023
We notice that Python 3.x and flair may fail to install Python dependencies on windows-latest due to potential compatibility issues with the latest Python versions on Windows. To fix this, I recommend to use Python 3.9 (_[News Updated:2023-10-24](#news/index.html#flair-005-development-version)_).



</div>

&nbsp;

-----


## Class and Object in R via {flaiR}

<div style="text-align: justify">

For R users, {`flairR`} is built on top of {reticulate}, enabling you to interact directly with Python modules in R and providing seamless support for documents in the R community. 

In the {`flairR`} architecture, we use the simplest S3 method to wrap both modules and methods within those modules, allowing R users to conveniently access and use Python functionalities. Here are the main modules and methods (functions) wrapped in {flairR}:



</div>

| **Wrapped Functions**                             | Corresponding Code Practice in Python                     | 
|---------------------------------------------------|-----------------------------------------------------------|
| `flair_datasets()`                                | from flair.datasets import *                              |
| `flair_data.Sentence()`                           | from flair.data import Sentence                           |
| `flair_nn()`                                      | from flair_nn import *                                    |
| `flair_nn.Classifier()`                           | from flair.embeddings import Classifier                   |
| `flair_embeddings()`                              | from flair.nn import *                                    |
| `flair_embeddings.FlairEmbeddings()`              | from flair.embeddings import FlairEmbeddings              |
| `flair_embeddings.TransformerWordEmbeddings()`    | from flair.embeddings import TransformerWordEmbeddings    |
| `flair_embeddings.WordEmbeddings()`               | from flair.embeddings import WordEmbeddings               |
| `flair_embeddings.TransformerDocumentEmbeddings()`| from flair.embeddings import TransformerDocumentEmbeddings|
| `flair_splitter()`                                | import flair.splitter                                     |
| `flair_splitter.SegtokSentenceSplitter()`         | from flair.models import  SegtokSentenceSplitter          |
| `flair_models.Sequencetagger()`                   | from flair.models import SequenceTagger                   |
| `flair_trainers()`                                | import flair.trainers                                     |
| `flair_models()`                                  | import flair.models                                       |
| `flair_models.TextClassifier()`                   | from flair.models import TextClassifier                   |
 
 
 

__Please note that the following basic examples are derived from the official [Flair NLP](https://flairnlp.github.io/docs/intro) Python documentation and tutorial.__

&nbsp;


### __Tag Entities in Text__ 

<div style="text-align: justify">

Let's run named entity recognition over the following example sentence: "I love Berlin and New York. To do this, all you need is to make a Sentence for this text, load a pre-trained model and use it to predict tags for the sentence object.

```{r}
# attach flaiR in R
library(flaiR)

# make a sentence

Sentence <- flair_data()$Sentence
sentence <- Sentence('I love Berlin and New York.')

# load the NER tagger
Classifier <- flair_nn()$Classifier
tagger <- Classifier$load('ner')

# run NER over sentence
tagger$predict(sentence)
```

This should print:
```{r}
# print the sentence with all annotations
print(sentence)
```

Use a for loop to print out each POS tag. It's important to note that Python is indexed from 0. Therefore, in an R environment, we must use `seq_along(sentence$get_labels()) - 1`.

```{r}
for (i in seq_along(sentence$get_labels())) {
      print(sentence$get_labels()[[i]])
  }
```

</div>

&nbsp;

### __Tag Part-of-Speech in Text__ 

<div style="text-align: justify">

We use flair/pos-english for POS tagging in the standard models on Hugging Face.
```{r}
# attach flaiR in R
library(flaiR)

# make a sentence
Sentence <- flair_data()$Sentence
sentence <- Sentence('I love Berlin and New York.')

# load the NER tagger
Classifier <- flair_nn()$Classifier
tagger <- Classifier$load('pos')

# run NER over sentence
tagger$predict(sentence)
```

This should print:

```{r}
# print the sentence with all annotations
print(sentence)
```

Use a for loop to print out each pos tag.
```{r}
for (i in seq_along(sentence$get_labels())) {
      print(sentence$get_labels()[[i]])
  }
```

</div>

&nbsp;

### __Detect Sentiment__

<div style="text-align: justify">

Let's run sentiment analysis over the same sentence to determine whether it is POSITIVE or NEGATIVE.

You can do this with essentially the same code as above. Just instead of loading the 'ner' model, you now load the 'sentiment' model:

```{r}
# attach flaiR in R
library(flaiR)

# make a sentence
Sentence <- flair_data()$Sentence
sentence <- Sentence('I love Berlin and New York.')

# load the flair_nn.classifier_load tagger
Classifier <- flair_nn()$Classifier
tagger <- Classifier$load('sentiment')

# run sentiment analysis over sentence
tagger$predict(sentence)
```

```{r}
# print the sentence with all annotations
print(sentence)
```

</div>

&nbsp;


### __Embeddings__

__Embeddings Words with Transformers__

<div style="text-align: justify">

Let's use a standard BERT model (bert-base-uncased) to embed the sentence "the grass is green".
Simply instantate `flair_embeddings.TransformerWordEmbeddings()`and use `$embed()` over the sentence object:

```{r}
# attach flaiR in R
library(flaiR)

# initiate TransformerWordEmbeddings
TransformerWordEmbeddings <- flair_embeddings()$TransformerWordEmbeddings
embedding <- TransformerWordEmbeddings('bert-base-uncased')

# create a sentence
sentence <- flair_data.Sentence('The grass is green .')

# embed words in sentence
embedding$embed(sentence)
```

This will cause each word in the sentence to be embedded. You can iterate through the words and get each embedding like this:
```{r}
for (i in seq_along(sentence$tokens)) {
  cat("Token: ",  reticulate::py_str(sentence$tokens[[i]]), "\n")
  # Access the embedding of the token, converting it to an R object, 
  # and print the first 15 elements of the vector.
  token_embedding <- sentence$tokens[[1]]$embedding
  print(head(token_embedding, 15))
}
```

</div>

&nbsp;

__Embeddings Documents with Transformers__

<div style="text-align: justify">

Sometimes you want to have an embedding for a whole document, not only individual words. In this case, use one of the DocumentEmbeddings classes in Flair. Let's again use a standard BERT model to get an embedding for the entire sentence:

```{r}
# initiate TransformerWordEmbeddings
embedding <- flair_embeddings.TransformerDocumentEmbeddings('bert-base-uncased')

# create a sentence
sentence <- flair_data.Sentence('The grass is green .')

# embed words in sentence
embedding$embed(sentence)
```

Use the `$embedding` method to extract the entire embedding from the sentence and print the embedding as follows:

```{r}
print(head(sentence$embedding, n = 20))
```

</div>

&nbsp;

__How to Stack Embeddings__

<div style="text-align: justify">


Flair allows you to combine embeddings into "embedding stacks". When not fine-tuning, using combinations of embeddings often gives best results!

Use the `StackedEmbeddings` class and instantiate it by passing a list of embeddings that you wish to combine. For instance, lets combine classic `GloVe` embeddings with `forward` and `backward` Flair embeddings.

First, instantiate the two embeddings you wish to combine:

```{r}
# init standard GloVe embedding
glove_embedding <- flair_embeddings.WordEmbeddings('glove')

# init Flair forward and backwards embeddings
flair_embedding_forward <- flair_embeddings.FlairEmbeddings('news-forward')
flair_embedding_backward <- flair_embeddings.FlairEmbeddings('news-backward')
```

Now, instantiate the `StackedEmbeddings` class and pass a list containing these two embeddings. Both R and Python have list functionality. Let's create a StackedEmbedding object that combines the GloVe and forward/backward Flair embeddings.
```{r}
stacked_embeddings <- flair_embeddings()$StackedEmbeddings(
  list(glove_embedding,
       flair_embedding_forward, 
       flair_embedding_backward))
```


Next, use the `$embed()` method to transform text into vectors for your sentences.
```{r}
# make a sentence
sentence <- flair_data.Sentence('I love Berlin and New York.')

# just embed a sentence using the StackedEmbedding as you would with any single embedding.
stacked_embeddings$embed(sentence)
```


Words are now embedded using a concatenation of three different embeddings. This means that the resulting embedding vector is still a single PyTorch vector.


```{r}
for (i in seq_along(sentence$tokens)) {
  cat("Token: ",  reticulate::py_str(sentence$tokens[[i]]), "\n")
  # Access the embedding of the token, converting it to an R object, 
  # and print the first 15 elements of the vector.
  token_embedding <- sentence$tokens[[1]]$embedding
  print(head(token_embedding, 15))
}
```

</div>

&nbsp;

-----

## Expanded Feats in flaiR

<div style="text-align: justify">


To enhance more efficient utilization in social science research, {flairR} extends FlairNLP with three principal functions to extract features in a neat format with [data.table](https://cran.r-project.org/web/packages/data.table/index.html). Through these featured functions, you don't have to write loops to format parsed output on your own; {`flairR`} will automatically do it for you in a neat format. The main features include [**part-of-speech tagging**](https://davidycliao.github.io/flaiR/articles/get_pos.html), [**transformer-based sentiment analysis**](https://davidycliao.github.io/flaiR/articles/get_entities.html), and [**named entity recognition**](https://davidycliao.github.io/flaiR/articles/get_sentiments.html). In addition, to handle the load on RAM when dealing with larger corpus, {`flairR`}  supports batch processing to handle texts in batches, which is especially useful when dealing with large datasets, to optimize memory usage and performance.


| **Core  Featured Function in flaiR**                    | Loader                     | Supported Models from Flair NLP                                                                                                        |
|----------------------------------------------|----------------------------|--------------------------------------------------------------------------------------------------------------------------|
| `get_entities()`, `get_entities_batch()`     | `load_tagger_ner()`        | `en` (English), `fr` (French), `da` (Danish), `nl` (Dutch), and more.                                                    |
| `get_pos()`, `get_pos_batch()`               | `load_tagger_pos()`        | `pos` (English POS), `fr-pos` (French POS), `de-pos` (German POS), `nl-pos` (Dutch POS), and more.                       |
| `get_sentiments()`, `get_sentiments_batch()` | `load_tagger_sentiments()` | `sentiment` (English) , `sentiment-fast `(English) , `de-offensive-language` (German offensive language detection model) |

</div>

&nbsp;


### __Tagging Parts-of-Speech with Flair Models__

<div style="text-align: justify">


You can load the pre-trained model `"pos-fast"`. For more pre-trained models, see https://flairnlp.github.io/docs/tutorial-basics/part-of-speech-tagging#-in-english.

```{r}
texts <- c("UCD is one of the best universities in Ireland.",
           "UCD has a good campus but is very far from my apartment in Dublin.",
           "Essex is famous for social science research.",
           "Essex is not in the Russell Group, but it is famous for political science research and in 1994 Group.",
           "TCD is the oldest university in Ireland.",
           "TCD is similar to Oxford.")

doc_ids <- c("doc1", "doc2", "doc3", "doc4", "doc5", "doc6")
```

```{r}
library(flaiR)
```

```{r}
tagger_pos <- load_tagger_pos("pos-fast")
```

```{r}
results <- get_pos(texts, doc_ids, tagger_pos)
head(results, n = 10)
```

</div>

&nbsp;

### __Tagging Entities with Flair Models__

<div style="text-align: justify">

Load the pretrained model `ner`. For more pretrained models, see https://flairnlp.github.io/docs/tutorial-basics/tagging-entities.


```{r}
library(flaiR)
```

```{r}
tagger_ner <- load_tagger_ner("ner")
```

```{r}
results <- get_entities(texts, doc_ids, tagger_ner)
head(results, n = 10)
```

</div>

&nbsp;


### __Tagging Sentiment__

<div style="text-align: justify">


Load the pretrained model "`sentiment`". The pre-trained models of "`sentiment`", "`sentiment-fast`", and "`de-offensive-language`" are currently available. For more pre-trained models, see https://flairnlp.github.io/docs/tutorial-basics/tagging-sentiment.


```{r}
library(flaiR)
```

```{r}
tagger_sent <- load_tagger_sentiments("sentiment")
```

```{r}
results <- get_sentiments(texts, doc_ids, tagger_sent)
head(results, n = 10)
```

</div>

&nbsp;

-----


## How to Contribute

<div style="text-align: justify">

R developers who want to contribute to {`flaiR`} are welcome – {`flaiR`} is an open source project. I warmly invite R users who share similar interests to join in contributing to this package. Please feel free to shoot me an email to collaborate on the task. Contributions – whether they be comments, code suggestions, tutorial examples, or forking the repository – are greatly appreciated. Please note that the `flaiR` is released with the [Contributor Code of Conduct](https://github.com/davidycliao/flaiR/blob/master/CONDUCT.md). By contributing to this project, you agree to abide by its terms. 

The primary communication channel for R users can be found [here](https://github.com/davidycliao/flaiR/discussions). Please feel free to share your insights on the [Discussion](https://github.com/davidycliao/flaiR/discussions) page and report any issues related to the R interface in the [Issue](https://github.com/davidycliao/flaiR/issues) section.


</div>




