---
title: "Quick Start"
# author: 
#   - name: "David (Yen-Chieh) Liao"
#     affiliation: "Postdoc at Text & Policy Research Group and SPIRe in UCD"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick Start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r include=FALSE}
# library(reticulate)
# library(flaiR)
# # reticulate::py_install("flair")
# system(paste(reticulate::py_config()$python, "-m pip install flair"))
system(paste(Sys.which("python3"), "-m pip install --upgrade pip"))
system(paste(Sys.which("python3"), "-m pip install torch"))
system(paste(Sys.which("python3"), "-m pip install flair"))
Sys.setenv(RETICULATE_PYTHON = Sys.which("python3"))
library(flaiR)
```


<div style="text-align: justify">

Flair is a Python library developed by [Zalando Research](https://engineering.zalando.com/posts/2018/11/zalando-research-releases-flair.html) that stands out as a notably user-friendly NLP framework. Flair NLP provides intuitive interfaces with exceptional multilingual embeddings, especially for various multilingual embedding frameworks like GloVe and transformer-based models on Hugging Face.

</div>


## flaiR Installation


__Required Software__

- Python >= 3.10
- R >= 4.2.0
- Rstudio

### Operating System

__macOS Terminal Installation__

Install Python 3.10 or higher.

```bash
brew install python@3.10

# Verify Python installation
python3 --version

# Install R
brew install R

# Verify R installation
R --version

# Install RStudio
brew install --cask rstudio
```

__PowerShell for Windows__

```bash
# Download Python installer from python.org and run:
# https://www.python.org/downloads/

# Verify Python installation
python --version

# Install R
# Download R installer from CRAN and run:
# https://cran.r-project.org/bin/windows/base/

# Verify R installation
R --version
```

__Docker Installation & Usage__

- Intel/AMD Processors:

```bash
# Pull and run
docker pull ghcr.io/davidycliao/flair-rstudio:latest
docker run -p 8787:8787 ghcr.io/davidycliao/flair-rstudio:latest
```

- Apple Silicon (M1/M2 Mac):
```bash
# Pull and run with platform specification
docker pull --platform linux/amd64 ghcr.io/davidycliao/flair-rstudio:latest
docker run --platform linux/amd64 -p 8787:8787 ghcr.io/davidycliao/flair-rstudio:latest
```

__Access RStudio Server:__
- Open browser: `http://localhost:8787`
- Username: `rstudio`
- Password: `rstudio123`


### R Package Installation

The `faiR` Will:

- Automatically check Python environment
- Install required Python packages (flair and its dependencies)
- Configure the Python-R connection

```r
install.packages("remotes")
remotes::install_github("davidycliao/flaiR", force = TRUE)
```

__R Version Dependencies__

The Matrix R package corresponds to different R versions:

- R 4.4.0+: Latest Matrix package version
- R 4.3.x: Matrix 1.5-1
- R 4.2.x: Matrix 1.4-1

<div style="text-align: justify">
Installation should work automatically as RStudio and R handle the dependencies. However, if you encounter Matrix package compilation errors, you might need the following setup:
</div>

- Install compiler tools (if needed) in the Terminal:

```bash
brew install gcc
```
- Configure R compiler settings:

```bash
mkdir -p ~/.R
touch ~/.R/Makevars
echo "FC=$(brew --prefix)/bin/gfortran" >> ~/.R/Makevars
echo "F77=$(brew --prefix)/bin/gfortran" >> ~/.R/Makevars
echo "FLIBS=-L$(brew --prefix)/lib/gcc/current -lgfortran -lquadmath -lm" >> ~/.R/Makevars
```

__Python Dependencies__

<div style="text-align: justify">

The following Python packages will be installed automatically by flaiR:

- flair
- scipy==1.12.0
- gensim==4.3.2

`flaiR` will automatically detect and configure your Python environment:

1. Checks for Python 3.10 or higher
2. Installs required Python packages
3. Configures R-Python interface using reticulate

Note: You can manage Python settings in RStudio through _Tools -> Global Options -> Python_. To check your Python configuration, use:

</div>

```r
reticulate::py_config()
```

### Recommended Configurations

For stable usage, we strongly recommend installing these specific versions.

| OS      | R Versions                 | Python Version |
|---------|----------------------------|----------------|
| Mac     | 4.3.2, 4.2.0, 4.2.1        | 3.10.x         |
| Mac     | Latest                     | 3.9            |
| Windows | 4.0.5                      | 3.10.x         |
| Windows | Latest                     | 3.9            |
| Ubuntu  | 4.3.2, 4.2.0, 4.2.1        | 3.10.x         |
| Ubuntu  | Latest                     | 3.9            |

__Note__: For Mac M1/M2 users, avoid R 4.2.1 due to potential gfortran compatibility issues.


### Troubleshooting

<div style="text-align: justify">


If you encounter any problems or have questions:

- Check the documentation
- Visit our Issues page
- Join our [Discussion forum](https://github.com/davidycliao/flaiR/discussions)

</div>


&nbsp;

-----

## NLP Tasks

<div style="text-align: justify">

For R users, flairR extends FlairNLP with three NLP task functions to extract features in a neat format with [data.table](https://cran.r-project.org/web/packages/data.table/index.html). Through these featured functions, you don't have to write loops to format parsed output on your own. The main features include part-of-speech tagging, named entity recognition and sentiment analysis. Additionally, to handle the load on RAM when dealing with larger corpora, flairR supports batch processing to handle texts in batches, which is especially useful when dealing with large datasets, to optimize memory usage and performance.

| **Core  Featured Functions**                    | Loader                     | Supported Models from Flair NLP                                                                                                        |
|----------------------------------------------|----------------------------|--------------------------------------------------------------------------------------------------------------------------|
| `get_entities()`, `get_entities_batch()`     | `load_tagger_ner()`        | `en` (English), `fr` (French), `da` (Danish), `nl` (Dutch), and more.                                                    |
| `get_pos()`, `get_pos_batch()`               | `load_tagger_pos()`        | `pos` (English POS), `fr-pos` (French POS), `de-pos` (German POS), `nl-pos` (Dutch POS), and more.                       |
| `get_sentiments()`, `get_sentiments_batch()` | `load_tagger_sentiments()` | `sentiment` (English) , `sentiment-fast `(English) , `de-offensive-language` (German offensive language detection model) |

</div>

&nbsp;


## Training and Fine-tuning

<div style="text-align: justify">

In __flairR__, we use the simplest __S3__ method to wrap major modules. All modules will work like [R6](https://bookdown.dongzhuoer.com/hadley/adv-r/s3-r6) in the R environment when loaded from Flair NLP. In Python, both functions and methods (sometimes referred to as functions in R) within a class can be accessed using the `$` operator. For example, `from flair.trainers import ModelTrainer` in Python is equivalent to `ModelTrainer <- flair_trainers()$ModelTrainer` in  R environment with __flairR__.

</div>

| **Wrapped Flair NLP Modules with S3**             | Corresponding Code Practices When Loading Modules from FlairNLP  | 
|---------------------------------------------------|------------------------------------------------------------------|
| `flair_datasets()`                                | from flair.datasets import *                                     |
| `flair_nn()`                                      | from flair.nn import *                                           |
| `flair_splitter()`                                | from flair.splitter import *                                     |
| `flair_trainers()`                                | from flair.trainers import *                                     |
| `flair_models()`                                  | from flair.models import *                                       |
 

&nbsp;

-----


