---
title: "Flair Base Types"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Flair Base Types}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, include = FALSE}
library(flaiR)
library(reticulate)
# system(paste(reticulate::py_config()$python, "-m pip install flair"))
reticulate::py_install("flair")
```


## Create Sentence Object

<div style="text-align: justify">

We will utilize {reticulate} to systematically use the Python flair package in our work. Firstly, For example, let's create a simple `sentence` class and check its string representation"


```{r}
library(flaiR)
string <- "What I see in UCD today, what I have seen of UCD in its impact on my own life and the life of Ireland, and what I want to see into the future is a university that can and does land real positive change in the world."
sentence <- flair_data.sentence(string)
```

```{r}
print(sentence)
```

</div>

&nbsp;

## Tokens in `Senetence` Object


```{r}
head(sentence$tokens)
```


__Retrieve the Token__

<div style="text-align: justify">

The Sentence object encompasses various methods and properties. In this instance, despite the Sentence object being imported into R, it genuinely belongs to a Python class; however, its concept aligns closely with R6. To comprehend the string representation format of the Sentence object, tagging at least one token is adequate. The `get_token(n)` method, a Python method, allows us to retrieve the Token object for a particular token. Additionally, we can use `[]` to index a specific token. It is noteworthy that Python indexes from 0, whereas R starts indexing from 1.



```{r}
# method in Python
sentence$get_token(5)
```


```{r}
# indexing in R 
sentence[4]
```
</div>


__Annotate POS tag and NER tag__

<div style="text-align: justify">


The `add_label(label_type, value)` method can be employed to assign a label to the token. We manually add a tag in this preliminary tutorial, so usually, in Universal POS tags, if `sentence[10]` is 'see', 'seen' might be tagged as `VERB`, indicating it is a past participle form of a verb.


```{r}
sentence[10]$add_label('manual-pos', 'VERB')
```


```{r}
print(sentence[10])
```

We can also add a NER (Named Entity Recognition) tag to `sentence[4]`, "UCD", identifying it as a university in Dublin.

```{r}
sentence[4]$add_label('ner', 'ORG')
```

```{r}
print(sentence[4])
```

If we print the sentence object, `Sentence[50]` provides information for 50 tokens → ['in'/ORG, 'seen'/VERB], thus displaying two tagging pieces of information.

```{r}
print(sentence)
```

</div>







