---
title: "Tutorial"
author: 
  - name: "Yen-Chieh Liao"
    affiliation: "University of Birmingham"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, include = FALSE}
# system(paste(Sys.which("python3"), "-m pip install --upgrade pip"))
# system(paste(Sys.which("python3"), "-m pip install torch"))
# system(paste(Sys.which("python3"), "-m pip install transformers==4.5.0"))
# system(paste(Sys.which("python3"), "-m pip install flair"))
# Sys.setenv(RETICULATE_PYTHON = Sys.which("python3"))
library(flaiR)
library(reticulate)
# remotes::install_github("prodriguezsosa/conText", force = TRUE)
# renv::install("prodriguezsosa/conText")

# system(paste(reticulate::py_config()$python, "-m pip install flair"))
# reticulate::py_install("flair")
# Sys.setenv(FLAIR_CACHE_ROOT = path.expand("~/.cache/flair"))
```

# Flair NLP and flaiR for Social Science

<div style="text-align: justify;">

Flair NLP is an open-source Natural Language Processing (NLP) library developed by [Zalando Research](https://github.com/zalandoresearch/). Known for its state-of-the-art solutions, it excels in contextual string embeddings, Named Entity Recognition (NER), and Part-of-Speech tagging (POS). Flair offers robust text analysis tools through multiple embedding approaches, including Flair contextual string embeddings, transformer-based embeddings from Hugging Face, and traditional models like GloVe and fasttext. Additionally, it provides pre-trained models for various languages and seamless integration with fine-tuned transformers hosted on Hugging Face. 

flaiR bridges these powerful NLP features from Python to the R environment, making advanced text analysis accessible for social science researcher by combining Flair's ease of use with R's familiar interface for integration with popular R packages such as [quanteda](https://quanteda.io) and more.

</div>

# The Overview

- [**Sentence and Token Object in FlaiR**](#tutorial.html#sentence-and-token)

- [**Sequence Taggings**](#tutorial.html#sequence-taggings)

- [**The Overview of Embedding**](#tutorial.html#the-overview-of-embedding)

- [**Embedding Examples**](#tutorial.html#embedding-examples)

- [**Performing NER Tasks**](#tutorial.html#performing-ner-tasks)

- [**Training a Binary Classifier in flaiR**](#tutorial.html#training-a-binary-classifier-in-flair)

- [**Training RNNa**](#tutorial.html#training-rnns)

- [**Finetune BERT**](#tutorial.html#finetune-transformers)

- [**Extending conText's Embedding Regression**](#tutorial.html#extending-contexts-embedding-regression)

&nbsp;

-----


# Sentence and Token

Sentence and Token are fundamental classes.

## Sentence

<div style="text-align: justify;">

A Sentence in Flair is an object that contains a sequence of Token objects, and it can be annotated with labels, such as named entities, part-of-speech tags, and more. It also can store embeddings for the sentence as a whole and different kinds of linguistic annotations.

Here's a simple example of how you create a Sentence:
</div>

```{r}
# Creating a Sentence object
library(flaiR)
string <- "What I see in UCD today, what I have seen of UCD in its impact on my own life and the life of Ireland."
Sentence <- flair_data()$Sentence
sentence <- Sentence(string)
```

`Sentence[26]` means that there are a total of 26 tokens in the sentence.

```{r}
print(sentence)
```


## Token

<div style="text-align: justify;">

When you use Flair to handle text data,[^1] `Sentence` and `Token` objects often play central roles in many use cases. When you create a Sentence object, it automatically tokenizes the text, removing the need to create the Token object manually.

Unlike R, which indexes from 1, Python indexes from 0. Therefore, when using a for loop, I use `seq_along(sentence) - 1`. The output should be something like:

</div>

```{r}
# The Sentence object has automatically created and contains multiple Token objects
# We can iterate through the Sentence object to view each Token

for (i in seq_along(sentence)-1) {
  print(sentence[[i]])
}
```

Or you can directly use `$tokens` method to print all tokens.

```{r}
print(sentence$tokens)
```


**Retrieve the Token**

<div style="text-align: justify;">

To comprehend the string representation format of the Sentence object, tagging at least one token is adequate. Python's `get_token(n)` method allows us to retrieve the Token object for a particular token. Additionally, we can use **`[]`** to index a specific token.

</div>


```{r}
# method in Python
sentence$get_token(5)
```

```{r}
# indexing in R 
sentence[6]
```

<div style="text-align: justify;">

Each word (and punctuation) in the text is treated as an individual Token object. These Token objects store text information and other possible linguistic information (such as part-of-speech tags or named entity tags) and embedding (if you used a model to generate them).

While you do not need to create Token objects manually, understanding how to manage them is useful in situations where you might want to fine-tune the tokenization process. For example, you can control the exactness of tokenization by manually creating Token objects from a Sentence object.

This makes Flair very flexible when handling text data since the automatic tokenization feature can be used for rapid development, while also allowing users to fine-tune their tokenization.

</div>

**Annotate POS tag and NER tag**

<div style="text-align: justify;">

The `add_label(label_type, value)` method can be employed to assign a label to the token. In Universal POS tags, if `sentence[10]` is 'see', 'seen' might be tagged as `VERB`, indicating it is a past participle form of a verb.

</div>

```{r}
sentence[10]$add_label('manual-pos', 'VERB')
```

```{r}
print(sentence[10])
```

<div style="text-align: justify;">

We can also add a NER (Named Entity Recognition) tag to `sentence[4]`, "UCD", identifying it as a university in Dublin.

</div>

```{r}
sentence[4]$add_label('ner', 'ORG')
```

```{r}
print(sentence[4])
```

<div style="text-align: justify;">

If we print the sentence object, `Sentence[50]` provides information for 50 tokens → ['in'/ORG, 'seen'/VERB], thus displaying two tagging pieces of information.

</div>

```{r}
print(sentence)
```

[^1]: Flair is built on PyTorch, which is a library in Python.


## Corpus

The Corpus object in Flair is a fundamental data structure that represents a dataset containing text samples, usually comprising of a training set, a development set (or validation set), and a test set. It's designed to work smoothly with Flair's models for tasks like named entity recognition, text classification, and more.

**Attributes:**

-   `train`: A list of sentences (List[Sentence]) that form the training dataset.
-   `dev` (or development): A list of sentences (List[Sentence]) that form the development (or validation) dataset.
-   `test`: A list of sentences (List[Sentence]) that form the test dataset.

**Important Methods:**

- `downsample`: This method allows you to downsample (reduce) the number of sentences in the train, dev, and test splits.
- `obtain_statistics`: This method gives a quick overview of the statistics of the corpus, including the number of sentences and the distribution of labels.
- `make_vocab_dictionary`: Used to create a vocabulary dictionary from the corpus.

```{r}
library(flaiR)
Corpus <- flair_data()$Corpus
Sentence <- flair_data()$Sentence
```

```{r}
# Create some example sentences
train <- list(Sentence('This is a training example.'))
dev <-  list(Sentence('This is a validation example.'))
test <- list(Sentence('This is a test example.'))

# Create a corpus using the custom data splits
corp <-  Corpus(train = train, dev = dev, test = test)
```

<div style="text-align: justify;">

`$obtain_statistics()` method of the Corpus object in the Flair library provides an overview of the dataset statistics. The method returns a [Python dictionary](https://www.w3schools.com/python/python_dictionaries.asp) with details about the training, validation (development), and test datasets that make up the corpus. In R, you can use the jsonlite package to format JSON.

</div>

```{r}
library(jsonlite)
data <- fromJSON(corp$obtain_statistics())
formatted_str <- toJSON(data, pretty=TRUE)
print(formatted_str)
```

**In R**

<div style="text-align: justify;">

Below, we use data from the article [*The Temporal Focus of Campaign Communication*](https://www.google.com/url?sa=t&rct=j&q=&esrc=s&source=web&cd=&ved=2ahUKEwjz_bS3p5KCAxWEWEEAHcuVAi4QFnoECA8QAQ&url=https%3A%2F%2Fwww.journals.uchicago.edu%2Fdoi%2Ffull%2F10.1086%2F715165&usg=AOvVaw3f_J3sXTrym2ZR64pF3ZtN&opi=89978449) by [Stefan Muller](https://muellerstefan.net), published in the *Journal of Politics* in 2020, as an example.

First, we vectorize the `cc_muller$text` using the Sentence function to transform it into a list object. Then, we reformat `cc_muller$class_pro_retro` as a factor. It's essential to note that R handles numerical values differently than Python. In R, numerical values are represented with a floating point, so it's advisable to convert them into factors or strings. Lastly, we employ the map function from the purrr package to assign labels to each sentence corpus using the `$add_label` method.

</div>

```{r}
library(purrr)
data(cc_muller)
# The `Sentence` object tokenizes text 
text <- lapply( cc_muller$text, Sentence)
# split sentence object to train and test. 
labels <- as.factor(cc_muller$class_pro_retro)
# `$add_label` method assigns the corresponding coded type to each Sentence corpus.
text <- map2(text, labels, ~ .x$add_label("classification", .y), .progress = TRUE)
```

To perform a train-test split using base R, we can follow these steps:

```{r}
set.seed(2046)
sample <- sample(c(TRUE, FALSE), length(text), replace=TRUE, prob=c(0.8, 0.2))
train  <- text[sample]
test   <- text[!sample]
sprintf("Corpus object sizes - Train: %d |  Test: %d", length(train), length(test))
```

<div style="text-align: justify;">

If you don't provide a dev set, flaiR will not force you to carve out a portion of your test set to serve as a dev set. However, in some cases when only the train and test sets are provided without a dev set, flaiR might automatically take a fraction of the train set (e.g., 10%) to use as a dev set ([#2259](https://github.com/flairNLP/flair/issues/2259#issuecomment-830040253)). This is to offer a mechanism for model selection and to prevent the model from overfitting on the train set.

In the "Corpus" function, there is a random selection of the `"dev"` dataset. To ensure reproducibility, we need to set the seed in the flaiR framework. We can accomplish this by calling the top-level module "flair" from flaiR and using `$set_seed(1964L)` to set the seed.

</div>

```{r}
flair <- import_flair()
flair$set_seed(1964L)
```

```{r}
corp <- Corpus(train=train, 
                 # dev=test,
                 test=test)
sprintf("Corpus object sizes - Train: %d | Test: %d | Dev: %d", 
        length(corp$train), 
        length(corp$test),
        length(corp$dev))
```

<div style="text-align: justify;">

In the later sections, there will be more similar processing using the `Corpus`. Following that, we will focus on advanced NLP applications.

</div>

&nbsp;

-----


# Sequence Taggings

## Tag Entities in Text


<div style="text-align: justify;">

Let's run named entity recognition over the following example sentence: "I love Berlin and New York". To do this, all you need to do is make a Sentence object for this text, load a pre-trained model and use it to predict tags for the object.

</div>



__NER Models__

| ID                  | Task              | Language         | Training Dataset            | Accuracy     | Contributor / Notes    |
|---------------------|-------------------|------------------|-----------------------------|--------------|------------------------|
| 'ner'               | NER (4-class)     | English          | Conll-03                    | 93.03 (F1)   |                        |
| 'ner-fast'          | NER (4-class)     | English          | Conll-03                    | 92.75 (F1)   | (fast model)           |
| 'ner-large'         | NER (4-class)     | English / Multilingual | Conll-03               | 94.09 (F1)   | (large model)         |
| 'ner-pooled'        | NER (4-class)     | English          | Conll-03                    | 93.24 (F1)   | (memory inefficient)   |
| 'ner-ontonotes'     | NER (18-class)    | English          | Ontonotes                   | 89.06 (F1)   |                        |
| 'ner-ontonotes-fast'| NER (18-class)    | English          | Ontonotes                   | 89.27 (F1)   | (fast model)           |
| 'ner-ontonotes-large'| NER (18-class)   | English / Multilingual | Ontonotes             | 90.93 (F1)   | (large model)          |
| 'ar-ner'            | NER (4-class)     | Arabic           | AQMAR & ANERcorp (curated)  | 86.66 (F1)   |                        |
| 'da-ner'            | NER (4-class)     | Danish           | Danish NER dataset          |              | AmaliePauli            |
| 'de-ner'            | NER (4-class)     | German           | Conll-03                    | 87.94 (F1)   |                        |
| 'de-ner-large'      | NER (4-class)     | German / Multilingual | Conll-03               | 92.31 (F1)   |                        |
| 'de-ner-germeval'   | NER (4-class)     | German           | Germeval                    | 84.90 (F1)   |                        |
| 'de-ner-legal'      | NER (legal text)  | German           | LER dataset                 | 96.35 (F1)   |                        |
| 'fr-ner'            | NER (4-class)     | French           | WikiNER (aij-wikiner-fr-wp3)| 95.57 (F1)   | mhham                  |
| 'es-ner-large'      | NER (4-class)     | Spanish          | CoNLL-03                    | 90.54 (F1)   | mhham                  |
| 'nl-ner'            | NER (4-class)     | Dutch            | CoNLL 2002                  | 92.58 (F1)   |                        |
| 'nl-ner-large'      | NER (4-class)     | Dutch            | Conll-03                    | 95.25 (F1)   |                        |
| 'nl-ner-rnn'        | NER (4-class)     | Dutch            | CoNLL 2002                  | 90.79 (F1)   |                        |
| 'ner-ukrainian'     | NER (4-class)     | Ukrainian        | NER-UK dataset              | 86.05 (F1)   | dchaplinsky             |


Source: https://flairnlp.github.io/docs/tutorial-basics/tagging-entities


__POS Models__

| ID              | Task                     | Language            | Training Dataset                  | Accuracy             | Contributor / Notes                 |
|-----------------|--------------------------|---------------------|-----------------------------------|----------------------|-------------------------------------|
| 'pos'           | POS-tagging              | English             | Ontonotes                         | 98.19 (Accuracy)     |                                     |
| 'pos-fast'      | POS-tagging              | English             | Ontonotes                         | 98.1 (Accuracy)      | (fast model)                        |
| 'upos'          | POS-tagging (universal)  | English             | Ontonotes                         | 98.6 (Accuracy)      |                                     |
| 'upos-fast'     | POS-tagging (universal)  | English             | Ontonotes                         | 98.47 (Accuracy)     | (fast model)                        |
| 'pos-multi'     | POS-tagging              | Multilingual        | UD Treebanks                      | 96.41 (average acc.) | (12 languages)                      |
| 'pos-multi-fast'| POS-tagging              | Multilingual        | UD Treebanks                      | 92.88 (average acc.) | (12 languages)                      |
| 'ar-pos'        | POS-tagging              | Arabic (+dialects)  | combination of corpora            |                      |                                     |
| 'de-pos'        | POS-tagging              | German              | UD German - HDT                   | 98.50 (Accuracy)     |                                     |
| 'de-pos-tweets' | POS-tagging              | German              | German Tweets                     | 93.06 (Accuracy)     | stefan-it                           |
| 'da-pos'        | POS-tagging              | Danish              | Danish Dependency Treebank        |                      | AmaliePauli                         |
| 'ml-pos'        | POS-tagging              | Malayalam           | 30000 Malayalam sentences         | 83                   | sabiqueqb                           |
| 'ml-upos'       | POS-tagging              | Malayalam           | 30000 Malayalam sentences         | 87                   | sabiqueqb                           |
| 'pt-pos-clinical'|POS-tagging              | Portuguese          | PUCPR                             | 92.39                | LucasFerroHAILab for clinical texts|
| 'pos-ukrainian' | POS-tagging              | Ukrainian           | Ukrainian UD                      | 97.93 (F1)           | dchaplinsky                         |

Source: https://flairnlp.github.io/docs/tutorial-basics/part-of-speech-tagging



```{r}
# attach flaiR in R
library(flaiR)

# make a sentence

Sentence <- flair_data()$Sentence
sentence <- Sentence('I love Berlin and New York.')

# load the NER tagger
SequenceTagger <- flair_models()$SequenceTagger
tagger <- SequenceTagger$load('flair/ner-english')  

# run NER over sentence
tagger$predict(sentence)
```

To print all annotations:

```{r}
# print the sentence with all annotations
print(sentence)
```

<div style="text-align: justify;">

Use a for loop to print out each POS tag. It's important to note that Python is indexed from 0. Therefore, in an R environment, we must use `seq_along(sentence$get_labels()) - 1`.

</div>


```{r}
for (i in seq_along(sentence$get_labels())) {
      print(sentence$get_labels()[[i]])
  }
```


## Tag Part-of-Speech 

<div style="text-align: justify;">

We use `flaiR/POS-english` for POS tagging in the standard models on Hugging Face.

</div>

```{r}
# attach flaiR in R
library(flaiR)

# make a sentence
Sentence <- flair_data()$Sentence
sentence <- Sentence('I love Berlin and New York.')

# load the NER tagger
Classifier <- flair_nn()$Classifier
tagger <- Classifier$load('pos')

```

_Penn Treebank POS Tags Reference_


| Tag   | Description | Example |
|-------|-------------|---------|
| DT    | Determiner | the, a, these |
| NN    | Noun, singular | cat, tree |
| NNS   | Noun, plural | cats, trees |
| NNP   | Proper noun, singular | John, London |
| NNPS  | Proper noun, plural | Americans |
| VB    | Verb, base form | take |
| VBD   | Verb, past tense | took |
| VBG   | Verb, gerund/present participle | taking |
| VBN   | Verb, past participle | taken |
| VBP   | Verb, non-3rd person singular present | take |
| VBZ   | Verb, 3rd person singular present | takes |
| JJ    | Adjective | big |
| RB    | Adverb | quickly |
| O     | Other | - |
| ,     | Comma | , |
| .     | Period | . |
| :     | Colon | : |
| -LRB- | Left bracket | ( |
| -RRB- | Right bracket | ) |
| ``    | Opening quotation | " |
| ''    | Closing quotation | " |
| HYPH  | Hyphen | - |
| CD    | Cardinal number | 1, 2, 3 |
| IN    | Preposition | in, on, at |
| PRP   | Personal pronoun | I, you, he |
| PRP$  | Possessive pronoun | my, your |
| UH    | Interjection | oh, wow |
| FW    | Foreign word | café |
| SYM   | Symbol | +, % |


```{r}
# run NER over sentence
tagger$predict(sentence)
```

```{r}
# print the sentence with all annotations
print(sentence)
```

Use a for loop to print out each POS tag.

```{r}
for (i in seq_along(sentence$get_labels())) {
      print(sentence$get_labels()[[i]])
  }
```

## Detect Sentiment

<div style="text-align: justify;">

Let's run sentiment analysis over the same sentence to determine whether it is POSITIVE or NEGATIVE.

You can do this with essentially the same code as above. Instead of loading the 'ner' model, you now load the `'sentiment'` model:

</div>

```{r}
# attach flaiR in R
library(flaiR)

# make a sentence
Sentence <- flair_data()$Sentence
sentence <- Sentence('I love Berlin and New York.')

# load the Classifier tagger from flair.nn module
Classifier <- flair_nn()$Classifier
tagger <- Classifier$load('sentiment')

# run sentiment analysis over sentence
tagger$predict(sentence)
```

```{r}
# print the sentence with all annotations
print(sentence)
```


------------------------------------------------------------------------

## Dealing with Dataframe

### Parts-of-Speech Tagging Across Full DataFrame

<div style="text-align: justify;">

You can apply Part-of-Speech (POS) tagging across an entire DataFrame using Flair's pre-trained models. Let's walk through an example using the pos-fast model. You can apply Part-of-Speech (POS) tagging across an entire DataFrame using Flair's pre-trained models. Let's walk through an example using the pos-fast model.
First, let's load our required packages and sample data:

</div>

```{r}
library(flaiR)
data(uk_immigration)
uk_immigration <- uk_immigration[1:2,]
```

<div style="text-align: justify;">

For POS tagging, we'll use Flair's pre-trained model. The pos-fast model offers a good balance between speed and accuracy. For more pre-trained models, check out Flair's documentation at Flair POS Tagging Documentation. There are two ways to load the POS tagger:

</div>


- Load with tag dictionary display (default):



```{r}
tagger_pos <- load_tagger_pos("pos-fast")
```

This will show you all available POS tags grouped by categories (nouns, verbs, adjectives, etc.).

- Load without tag display for a cleaner output:

```{r}
pos_tagger <- load_tagger_pos("pos-fast", show_tags = FALSE)
```

Now we can process our texts:

```{r}
results <- get_pos(texts = uk_immigration$text,
                   doc_ids = uk_immigration$speaker,
                   show.text_id = TRUE,
                   tagger = pos_tagger)

head(results, n = 10)
```

### Tagging Entities Across Full DataFrame

<div style="text-align: justify;">

This section focuses on performing Named Entity Recognition (NER) on data stored in a dataframe format. My goal is to identify and tag named entities within text that is organized in a structured dataframe.

I load the flaiR package and use the built-in uk_immigration dataset. For demonstration purposes, I'm only taking the first two rows. This dataset contains discussions about immigration in the UK.

Load the pre-trained model `ner`. For more pre-trained models, see <https://flairnlp.github.io/docs/tutorial-basics/tagging-entities>.

</div>


```{r}
library(flaiR)
data(uk_immigration)
uk_immigration <- head(uk_immigration, n = 2)
```

<div style="text-align: justify;">

Next, I load the latest model hosted and maintained on Hugging Face by the Flair NLP team. For more Flair NER models, you can visit the official Flair NLP page on Hugging Face (https://huggingface.co/flair).

</div>

```{r}
# Load model without displaying tags
# tagger <- load_tagger_ner("flair/ner-english-large", show_tags = FALSE)

library(flaiR)
tagger_ner <- load_tagger_ner("flair/ner-english-ontonotes")
```

<div style="text-align: justify;">

I load a pre-trained NER model. Since I'm using a Mac M1/M2, I set the model to run on the MPS device for faster processing. If I want to use other pre-trained models, I can check the Flair documentation website for available options.

</div>

Now I'm ready to process the text:

```{r}
results <- get_entities(texts = uk_immigration$text,
                        doc_ids = uk_immigration$speaker,
                        tagger = tagger_ner,
                        batch_size = 2,
                        verbose = FALSE)
head(results, n = 10)
```



&nbsp;

-----

## Highlight Entities with Colors
<div style="text-align: justify;">

This tutorial demonstrates how to use the flaiR package to identify and highlight named entities (such as names, locations, organizations) in text.


<u>**Step 1**</u> Create Text with Named Entities

First, we load the flaiR package and work with a sample text:

</div>

```{r}
library(flaiR)
data("uk_immigration")
uk_immigration <- uk_immigration[30,]
tagger_ner <- load_tagger_ner("flair/ner-english-fast")

result <- get_entities(uk_immigration$text,
                       tagger = tagger_ner,
                       show.text_id = FALSE
                       )
```

<u>**Step 2**</u> Highlight the Named Entities

<div style="text-align: justify;">

Use the `highlight_text` function to color-code the identified entities:
</div>

```{r}
highlighted_text <- highlight_text(text = uk_immigration$text, 
                                   entities_mapping = map_entities(result))
highlighted_text
```



__Explanation:__

- `load_tagger_ner("ner")` loads the pre-trained NER model
- `get_entities()` identifies named entities in the text
- `map_entities()` maps the identified entities to colors
- `highlight_text()` marks the original text using these colors

<div style="text-align: justify;">
Each type of entity (such as person names, locations, organization names) will be displayed in a different color, making the named entities in the text immediately visible.

</div>


&nbsp;

-----


# The Overview of Embedding

<div style="text-align: justify">


All word embedding classes inherit from the `TokenEmbeddings` class and call the `embed()` method to embed the text. In most cases when using Flair, various and complex embedding processes are hidden behind the interface. Users simply need to instantiate the necessary embedding class and call `embed()` to embed text.

Here are the types of embeddings currently supported in FlairNLP: 


| Class | Type | Paper |
| ------------- | -------------  | -------------  |
| [`BytePairEmbeddings`](articles/transformer_wordembeddings.html#bytepairembeddings) | Subword-level word embeddings | [Heinzerling and Strube (2018)](https://www.aclweb.org/anthology/L18-1473)  |
| [`CharacterEmbeddings`]() | Task-trained character-level embeddings of words | [Lample et al. (2016)](https://www.aclweb.org/anthology/N16-1030) |
| [`ELMoEmbeddings`]() | Contextualized word-level embeddings | [Peters et al. (2018)](https://aclweb.org/anthology/N18-1202)  |
| [`FastTextEmbeddings`]() | Word embeddings with subword features | [Bojanowski et al. (2017)](https://aclweb.org/anthology/Q17-1010)  |
| [`FlairEmbeddings`](articles/transformer_wordembeddings.html#flair-embeddings) | Contextualized character-level embeddings | [Akbik et al. (2018)](https://www.aclweb.org/anthology/C18-1139/)  |
| [`OneHotEmbeddings`]() | Standard one-hot embeddings of text or tags | - |
| [`PooledFlairEmbeddings`](articles/transformer_wordembeddings.html#pooled-flair-embeddings) | Pooled variant of `FlairEmbeddings` |  [Akbik et al. (2019)](https://www.aclweb.org/anthology/N19-1078/)  |
| [`TransformerWordEmbeddings`](articles/transformer_wordembeddings.html#transformer-embeddings)) | Embeddings from pretrained [transformers](https://huggingface.co/transformers/pretrained_models.html) (BERT, XLM, GPT, RoBERTa, XLNet, DistilBERT etc.) | [Devlin et al. (2018)](https://www.aclweb.org/anthology/N19-1423/) [Radford et al. (2018)](https://d4mucfpksywv.cloudfront.net/better-language-models/language_models_are_unsupervised_multitask_learners.pdf)  [Liu et al. (2019)](https://arxiv.org/abs/1907.11692) [Dai et al. (2019)](https://arxiv.org/abs/1901.02860) [Yang et al. (2019)](https://arxiv.org/abs/1906.08237) [Lample and Conneau (2019)](https://arxiv.org/abs/1901.07291) |
| [`WordEmbeddings`](https://github.com/flairNLP/flair/tree/master/resources/docs/embeddings/CLASSIC_WORD_EMBEDDINGS.md) | Classic word embeddings |  |

</div>

&nbsp;

-----


## Byte Pair Embeddings 
<div style="text-align: justify">

_Please note that ihis document for R is a conversion of the  [Flair NLP](https://github.com/flairNLP/flair/blob/master/resources/docs/embeddings/BYTE_PAIR_EMBEDDINGS.md) document implemented in Python._



`BytePairEmbeddings` are word embeddings that operate at the subword level. They can embed any word by breaking it down into subwords and looking up their corresponding embeddings. This technique was introduced by [Heinzerling and Strube (2018)](https://www.aclweb.org/anthology/L18-1473) , who demonstrated that BytePairEmbeddings achieve comparable accuracy to traditional word embeddings while requiring only a fraction of the model size. This makes them an excellent choice for training compact models.

To initialize BytePairEmbeddings, you need to specify:

- A language code (275 languages supported)
- Number of syllables
- Number of dimensions (options: 50, 100, 200, or 300)

```{r include=FALSE}
# 在 R console 中執行
unlink("~/.cache/flair", recursive = TRUE)  
```


```{r}
library(flaiR)

# Initialize embedding
BytePairEmbeddings <- flair_embeddings()$BytePairEmbeddings

# Create BytePairEmbeddings with specified parameters
embedding <- BytePairEmbeddings(
    language = "en",        # Language code (e.g., "en" for English)
    dim = 50L,              # Embedding dimensions: options are 50L, 100L, 200L, or 300L
    syllables = 100000L     # Subword vocabulary size

)

# Create a sample sentence
Sentence <- flair_data()$Sentence
sentence = Sentence('The grass is green .')

# Embed words in the sentence
embedding$embed(sentence)

# Print embeddings 
for (i in 1:length(sentence$tokens)) {
    token <- sentence$tokens[[i]]
    cat("\nWord:", token$text, "\n")
    
    # Convert embedding to R vector and print
    # Python index starts from 0, so use i-1
    embedding_vector <- sentence[i-1]$embedding$numpy()
    cat("Embedding shape:", length(embedding_vector), "\n")
    cat("First 5 values:", head(embedding_vector, 5), "\n")
    cat("-------------------\n")
}
```


More information can be found on the [byte pair embeddings](https://nlp.h-its.org/bpemb/) web page. `BytePairEmbeddings` also have a multilingual model capable of embedding any word in any language.  You can instantiate it with:

```{r eval=FALSE, include=TRUE}
embedding <- BytePairEmbeddings('multi')
```

You can also load custom `BytePairEmbeddings` by specifying a path to model_file_path and embedding_file_path arguments. They correspond respectively to a `SentencePiece` model file and to an embedding file (Word2Vec plain text or GenSim binary). 

</div>


##  Flair Embeddings

<div style="text-align: justify">

__The following example manual is translated into R from Flair NLP by [Zalando Research](https://engineering.zalando.com/posts/2018/11/zalando-research-releases-flair.html).__ In Flair, the use of embedding is very quite straightforward. Here’s an example code snippet of how to use Flair’s contextual string embeddings:

```{r}
library(flaiR)
FlairEmbeddings <- flair_embeddings()$FlairEmbeddings
# init embedding
flair_embedding_forward <- FlairEmbeddings('news-forward')

# create a sentence
Sentence <- flair_data()$Sentence
sentence = Sentence('The grass is green .')

# embed words in sentence
flair_embedding_forward$embed(sentence)
```


| ID | Language | Embedding |
| -------------     | ------------- | ------------- |
| 'multi-X'    | 300+ | [JW300 corpus](http://opus.nlpl.eu/JW300.php), as proposed by [Agić and Vulić (2019)](https://www.aclweb.org/anthology/P19-1310/). The corpus is licensed under CC-BY-NC-SA
| 'multi-X-fast'    | English, German, French, Italian, Dutch, Polish | Mix of corpora (Web, Wikipedia, Subtitles, News), CPU-friendly |
| 'news-X'    | English | Trained with 1 billion word corpus |
| 'news-X-fast'    | English | Trained with 1 billion word corpus, CPU-friendly |
| 'mix-X'     | English | Trained with mixed corpus (Web, Wikipedia, Subtitles) |
| 'ar-X'     | Arabic | Added by [@stefan-it](https://github.com/zalandoresearch/flair/issues/614): Trained with Wikipedia/OPUS |
| 'bg-X'  | Bulgarian | Added by [@stefan-it](https://github.com/zalandoresearch/flair/issues/614): Trained with Wikipedia/OPUS |
| 'bg-X-fast'  | Bulgarian  | Added by [@stefan-it](https://github.com/stefan-it/flair-lms): Trained with various sources (Europarl, Wikipedia or SETimes) |
| 'cs-X'     | Czech | Added by [@stefan-it](https://github.com/zalandoresearch/flair/issues/614): Trained with Wikipedia/OPUS |
| 'cs-v0-X'    | Czech | Added by [@stefan-it](https://github.com/stefan-it/flair-lms): LM embeddings (earlier version) |
| 'de-X'  | German  | Trained with mixed corpus (Web, Wikipedia, Subtitles) |
| 'de-historic-ha-X'  | German (historical) | Added by [@stefan-it](https://github.com/stefan-it/flair-lms): Historical German trained over *Hamburger Anzeiger* |
| 'de-historic-wz-X'  | German (historical) | Added by [@stefan-it](https://github.com/stefan-it/flair-lms): Historical German trained over *Wiener Zeitung* |
| 'de-historic-rw-X'  | German (historical) | Added by [@redewiedergabe](https://github.com/redewiedergabe): Historical German trained over 100 million tokens |
| 'es-X'    | Spanish | Added by [@iamyihwa](https://github.com/zalandoresearch/flair/issues/80): Trained with Wikipedia |
| 'es-X-fast'    | Spanish | Added by [@iamyihwa](https://github.com/zalandoresearch/flair/issues/80): Trained with Wikipedia, CPU-friendly |
| 'es-clinical-'    | Spanish (clinical) | Added by [@matirojasg](https://github.com/flairNLP/flair/issues/2292): Trained with Wikipedia |
| 'eu-X'    | Basque | Added by [@stefan-it](https://github.com/zalandoresearch/flair/issues/614): Trained with Wikipedia/OPUS |
| 'eu-v0-X'    | Basque | Added by [@stefan-it](https://github.com/stefan-it/flair-lms): LM embeddings (earlier version) |
| 'fa-X'     | Persian | Added by [@stefan-it](https://github.com/zalandoresearch/flair/issues/614): Trained with Wikipedia/OPUS |
| 'fi-X'     | Finnish | Added by [@stefan-it](https://github.com/zalandoresearch/flair/issues/614): Trained with Wikipedia/OPUS |
| 'fr-X'    | French | Added by [@mhham](https://github.com/mhham): Trained with French Wikipedia |
| 'he-X'     | Hebrew | Added by [@stefan-it](https://github.com/zalandoresearch/flair/issues/614): Trained with Wikipedia/OPUS |
| 'hi-X'     | Hindi | Added by [@stefan-it](https://github.com/zalandoresearch/flair/issues/614): Trained with Wikipedia/OPUS |
| 'hr-X'     | Croatian | Added by [@stefan-it](https://github.com/zalandoresearch/flair/issues/614): Trained with Wikipedia/OPUS |
| 'id-X'     | Indonesian | Added by [@stefan-it](https://github.com/zalandoresearch/flair/issues/614): Trained with Wikipedia/OPUS |
| 'it-X'     | Italian | Added by [@stefan-it](https://github.com/zalandoresearch/flair/issues/614): Trained with Wikipedia/OPUS |
| 'ja-X'    | Japanese | Added by [@frtacoa](https://github.com/zalandoresearch/flair/issues/527): Trained with 439M words of Japanese Web crawls (2048 hidden states, 2 layers)|
| 'nl-X'     | Dutch | Added by [@stefan-it](https://github.com/zalandoresearch/flair/issues/614): Trained with Wikipedia/OPUS |
| 'nl-v0-X'    | Dutch | Added by [@stefan-it](https://github.com/stefan-it/flair-lms): LM embeddings (earlier version) |
| 'no-X'     | Norwegian | Added by [@stefan-it](https://github.com/zalandoresearch/flair/issues/614): Trained with Wikipedia/OPUS |
| 'pl-X'  | Polish  | Added by [@borchmann](https://github.com/applicaai/poleval-2018): Trained with web crawls (Polish part of CommonCrawl) |
| 'pl-opus-X'     | Polish | Added by [@stefan-it](https://github.com/zalandoresearch/flair/issues/614): Trained with Wikipedia/OPUS |
| 'pt-X'    | Portuguese | Added by [@ericlief](https://github.com/ericlief/language_models): LM embeddings |
| 'sl-X'     | Slovenian | Added by [@stefan-it](https://github.com/zalandoresearch/flair/issues/614): Trained with Wikipedia/OPUS |
| 'sl-v0-X'  | Slovenian  | Added by [@stefan-it](https://github.com/stefan-it/flair-lms): Trained with various sources (Europarl, Wikipedia and OpenSubtitles2018) |
| 'sv-X'    | Swedish | Added by [@stefan-it](https://github.com/zalandoresearch/flair/issues/614): Trained with Wikipedia/OPUS |
| 'sv-v0-X'    | Swedish | Added by [@stefan-it](https://github.com/stefan-it/flair-lms): Trained with various sources (Europarl, Wikipedia or OpenSubtitles2018) |
| 'ta-X'    | Tamil | Added by [@stefan-it](https://github.com/stefan-it/plur) |
| 'pubmed-X'    | English | Added by [@jessepeng](https://github.com/zalandoresearch/flair/pull/519): Trained with 5% of PubMed abstracts until 2015 (1150 hidden states, 3 layers)|
| 'de-impresso-hipe-v1-X' | German (historical)  | In-domain data (Swiss and Luxembourgish newspapers) for [CLEF HIPE Shared task](https://impresso.github.io/CLEF-HIPE-2020). More information on the shared task can be found in [this paper](https://zenodo.org/record/3752679#.XqgzxXUzZzU) |
| 'en-impresso-hipe-v1-X' | English (historical) | In-domain data (Chronicling America material) for [CLEF HIPE Shared task](https://impresso.github.io/CLEF-HIPE-2020). More information on the shared task can be found in [this paper](https://zenodo.org/record/3752679#.XqgzxXUzZzU) |
| 'fr-impresso-hipe-v1-X' | French (historical)  | In-domain data (Swiss and Luxembourgish newspapers) for [CLEF HIPE Shared task](https://impresso.github.io/CLEF-HIPE-2020). More information on the shared task can be found in [this paper](https://zenodo.org/record/3752679#.XqgzxXUzZzU) |
| 'am-X' | Amharic  | Based on 6.5m Amharic text corpus crawled from different sources. See [this paper](https://www.mdpi.com/1999-5903/13/11/275) and the official [GitHub Repository](https://github.com/uhh-lt/amharicmodels) for more information. |
| 'uk-X' | Ukrainian | Added by [@dchaplinsky](https://github.com/dchaplinsky): Trained with [UberText](https://lang.org.ua/en/corpora/) corpus. |

__Source__: [https://github.com/flairNLP/flair/blob/master/resources/docs/embeddings/FLAIR_EMBEDDINGS.md#flair-embeddings](https://github.com/flairNLP/flair/blob/master/resources/docs/embeddings/FLAIR_EMBEDDINGS.md#flair-embeddings)

</div>

<div style="text-align: justify">

So, if you want to load embeddings from the German forward LM model, instantiate the method as follows:
```{r}
flair_de_forward <- FlairEmbeddings('de-forward')
```

And if you want to load embeddings from the Bulgarian backward LM model, instantiate the method as follows:
```{r}
flair_bg_backward <- FlairEmbeddings('bg-backward')
```

</div>

&nbsp;

-----

##  Recommended Flair Usage in flaiR in R

<div style="text-align: justify">
We recommend combining both forward and backward Flair embeddings. Depending on the task, we also recommend adding standard word embeddings into the mix. So, our recommended `StackedEmbedding` for most English tasks is:

```{r}
FlairEmbeddings <- flair_embeddings()$FlairEmbeddings
WordEmbeddings <- flair_embeddings()$WordEmbeddings
StackedEmbeddings <- flair_embeddings()$StackedEmbeddings

# create a StackedEmbedding object that combines glove and forward/backward flair embeddings
stacked_embeddings <- StackedEmbeddings(list(WordEmbeddings("glove"),
                                             FlairEmbeddings("news-forward"),
                                             FlairEmbeddings("news-backward")))

```



That's it! Now just use this embedding like all the other embeddings, i.e. call the `embed()` method over your sentences.
```{r}
# create a sentence
Sentence <- flair_data()$Sentence
sentence = Sentence('The grass is green .')
```

```{r}
# just embed a sentence using the StackedEmbedding as you would with any single embedding.
stacked_embeddings$embed(sentence)
```

```{r}
# now check out the embedded tokens.
# Note that Python is indexing from 0. In an R for loop, using seq_along(sentence) - 1 achieves the same effect.
for (i in  seq_along(sentence)-1) {
  print(sentence[i])
  print(sentence[i]$embedding)
}
```

Words are now embedded using a concatenation of three different embeddings. This combination often gives state-of-the-art accuracy.

</div>

&nbsp;

-----


##  Pooled Flair Embeddings

<div style="text-align: justify">

We also developed a pooled variant of the `FlairEmbeddings`. These embeddings differ in that they *constantly evolve over time*, even at prediction time (i.e. after training is complete). This means that the same words in the same sentence at two different points in time may have different embeddings.

`PooledFlairEmbeddings` manage a 'global' representation of each distinct word by using a pooling operation of all past occurences. More details on how this works may be found in [Akbik et al. (2019)](https://www.aclweb.org/anthology/N19-1078/).

You can instantiate and use `PooledFlairEmbeddings` like any other embedding:


```{r}
# initiate embedding from Flair NLP
PooledFlairEmbeddings <- flair_embeddings()$PooledFlairEmbeddings
flair_embedding_forward <- PooledFlairEmbeddings('news-forward')

# create a sentence object
sentence <- Sentence('The grass is green .')

# embed words in sentence
flair_embedding_forward$embed(sentence)
```

Note that while we get some of our best results with `PooledFlairEmbeddings` they are very ineffective memory-wise since they keep past embeddings of all words in memory. In many cases, regular `FlairEmbeddings` will be nearly as good but with much lower memory requirements.


</div>

&nbsp;

-----

##  Transformer Embeddings


<div style="text-align: justify">

Please note that content and examples in this section have been extensively revised from the [`TransformerWordEmbeddings`](https://github.com/flairNLP/flair/tree/master/resources/docs/embeddings/TRANSFORMER_EMBEDDINGS.md) official documentation. Flair supports various Transformer-based architectures like BERT or XLNet from [HuggingFace](https://github.com/huggingface), 
with two classes [`TransformerWordEmbeddings`](#flair.embeddings.token.TransformerWordEmbeddings) (to embed words or tokens) and [`TransformerDocumentEmbeddings`](#flair.embeddings.document.TransformerDocumentEmbeddings) (to embed documents).

</div>

&nbsp;



## Embeddings Words with Transformers

<div style="text-align: justify">

For instance, to load a standard BERT transformer model, do:

```{r}
library(flaiR)
# initiate embedding and load BERT model from HugginFaces
TransformerWordEmbeddings <- flair_embeddings()$TransformerWordEmbeddings
embedding <- TransformerWordEmbeddings('bert-base-uncased')

# create a sentence
Sentence <- flair_data()$Sentence
sentence = Sentence('The grass is green .')

# embed words in sentence
embedding$embed(sentence)
```


If instead you want to use RoBERTa, do:
```{r}
TransformerWordEmbeddings <- flair_embeddings()$TransformerWordEmbeddings
embedding <- TransformerWordEmbeddings('roberta-base')
sentence <- Sentence('The grass is green .')
embedding$embed(sentence)
```

{`flaiR`} interacts with Flair NLP ([Zalando Research](https://github.com/zalandoresearch/)), allowing you to use pre-trained models from [HuggingFace](https://https://huggingface.co/models) , where you can search for models to use. 


## Embedding Documents with Transformers

To embed a whole sentence as one (instead of each word in the sentence), simply use the [`TransformerDocumentEmbeddings`](#flair.embeddings.document.TransformerDocumentEmbeddings) 
instead:

```{r}
TransformerDocumentEmbeddings <- flair_embeddings()$TransformerDocumentEmbeddings
embedding <- TransformerDocumentEmbeddings('roberta-base')
sentence <- Sentence('The grass is green.')
embedding$embed(sentence)
```


</div>

### Arguments

<div style="text-align: justify">


There are several options that you can set when you init the [`TransformerWordEmbeddings`](#flair.embeddings.token.TransformerWordEmbeddings) 
and [`TransformerDocumentEmbeddings`](#flair.embeddings.document.TransformerDocumentEmbeddings) classes:

| Argument               | Default              | Description
|------------------------|----------------------| ------------------------------------------------------------------------------
| `model`                | `bert-base-uncased`  | The string identifier of the transformer model you want to use (see above)
| `layers`               | `all`                | Defines the layers of the Transformer-based model that produce the embedding
| `subtoken_pooling`     | `first`              | See [Pooling operation section](#Pooling-operation).
| `layer_mean`           | `True`               | See [Layer mean section](#Layer-mean).
| `fine_tune`            | `False`              | Whether or not embeddings are fine-tuneable.
| `allow_long_sentences` | `True`               | Whether or not texts longer than maximal sequence length are supported.
| `use_context`          | `False`              | Set to True to include context outside of sentences. This can greatly increase accuracy on some tasks, but slows down embedding generation.

</div>

### Layers

<div style="text-align: justify">

The `layers` argument controls which transformer layers are used for the embedding. If you set this value to '-1,-2,-3,-4', the top 4 layers are used to make an embedding. If you set it to '-1', only the last layer is used. If you set it to "all", then all layers are used. This affects the length of an embedding, since layers are just concatenated.

```{r}
Sentence <- flair_data()$Sentence
TransformerWordEmbeddings <- flair_embeddings()$TransformerWordEmbeddings
sentence = Sentence('The grass is green.')

# use only last layers
embeddings <- TransformerWordEmbeddings('bert-base-uncased', layers='-1', layer_mean = FALSE)
embeddings$embed(sentence)
print(sentence[0]$embedding$size())

sentence$clear_embeddings()
```

```{r}
sentence <- Sentence('The grass is green.')

# use only last layers
embeddings <- TransformerWordEmbeddings('bert-base-uncased', layers = "-1", layer_mean = FALSE)
embeddings$embed(sentence)
print(sentence[0]$embedding$size())

sentence$clear_embeddings()

```


```{r}
# use last two layers
embeddings <- TransformerWordEmbeddings('bert-base-uncased', layers='-1,-2', layer_mean = FALSE)
embeddings$embed(sentence)
print(sentence[0]$embedding$size())

sentence$clear_embeddings()

```


```{r}
# use ALL layers
embeddings = TransformerWordEmbeddings('bert-base-uncased', layers='all', layer_mean=FALSE)
embeddings$embed(sentence)
print(sentence[0]$embedding$size())
```

Here's an example of how it might be done:

You can directly import torch from reticulate since it has already been installed through the flair dependency when you installed flair in Python.

```{r}
# You can directly import torch from reticulate since it has already been installed through the flair dependency when you installed flair in Python.
torch <- reticulate::import('torch')

# Attempting to create a tensor with integer dimensions
torch$Size(list(768L))
torch$Size(list(1536L))
torch$Size(list(9984L))
```


Notice the L after the numbers in the list? This ensures that R treats the numbers as integers. If you're generating these numbers dynamically (e.g., through computation), you might want to ensure they are integers before attempting to create the tensor. I.e. the size of the embedding increases the mode layers we use (but ONLY if layer_mean is set to False, otherwise the length is always the same).

</div>


### Pooling Operation

<div style="text-align: justify">

Most of the Transformer-based models use subword tokenization. E.g. the following
token `puppeteer` could be tokenized into the subwords: `pupp`, `##ete` and `##er`.

We implement different pooling operations for these subwords to generate the final token representation:

* `first`: only the embedding of the first subword is used
* `last`: only the embedding of the last subword is used
* `first_last`: embeddings of the first and last subwords are concatenated and used
* `mean`: a `torch.mean` over all subword embeddings is calculated and used

You can choose which one to use by passing this in the constructor:


```{r}
# use first and last subtoken for each word
embeddings = TransformerWordEmbeddings('bert-base-uncased', subtoken_pooling='first_last')
embeddings$embed(sentence)
print(sentence[0]$embedding$size())
```

</div>

### Layer Mean

<div style="text-align: justify">

The Transformer-based models have a certain number of layers. By default, all layers you select are
concatenated as explained above. Alternatively, you can set `layer_mean=True` to do a mean over all
selected layers. The resulting vector will then always have the same dimensionality as a single layer:

```{r}
# initiate embedding from transformer. This model will be downloaded from Flair NLP huggingface.
embeddings <- TransformerWordEmbeddings('bert-base-uncased', layers="all", layer_mean=TRUE)

# create a sentence object
sentence = Sentence("The Oktoberfest is the world's largest Volksfest .")

# embed words in sentence
embedding$embed(sentence)
```

</div>

## Fine-tuneable or Not
<div style="text-align: justify">

Here's an example of how it might be done: In some setups, you may wish to fine-tune the transformer embeddings. In this case, set `fine_tune=True` in the init method. When fine-tuning, you should also only use the topmost layer, so best set `layers='-1'`.
```{r}
# use first and last subtoken for each word
TransformerWordEmbeddings <- flair_embeddings()$TransformerWordEmbeddings
embeddings <- TransformerWordEmbeddings('bert-base-uncased', fine_tune=TRUE, layers='-1')
embeddings$embed(sentence)
```

This will print a tensor that now has a gradient function and can be fine-tuned if you use it in a training routine.


```{r}
print(sentence[0]$embedding)
```

<!-- ```python -->
<!-- tensor([-0.0323, -0.3904, -1.1946,  ...,  0.1305, -0.1365, -0.4323], -->
<!--        device='cuda:0', grad_fn=<CatBackward>) -->
<!-- ``` -->
</div>

__More Models__

<div style="text-align: justify">

Please have a look at the awesome [HuggingFace](https://huggingface.co/models) for all supported pre-trained models!

</div>



&nbsp;

-----
 

###  Classic Word Embeddings
<div style="text-align: justify">


Classic word embeddings are static and word-level, meaning that each distinct word gets exactly one pre-computed
embedding. Most embeddings fall under this class, including the popular GloVe or Komninos embeddings.

Simply instantiate the `WordEmbeddings` class and pass a string identifier of the embedding you wish to load. So, if
you want to use GloVe embeddings, pass the string 'glove' to the constructor:


```{r}
library(flaiR)
# initiate embedding with glove
WordEmbeddings <- flair_embeddings()$WordEmbeddings
glove_embedding <-  WordEmbeddings('glove')
```


Now, create an example sentence and call the embedding's `embed()` method. You can also pass a list of sentences to this method since some embedding types make use of batching to increase speed.


```{r}
library(flaiR)
# initiate a sentence object
Sentence <- flair_data()$Sentence

# create sentence object.
sentence = Sentence('The grass is green .')

# embed a sentence using glove.
glove_embedding$embed(sentence)
```

This prints out the tokens and their embeddings. GloVe embeddings are Pytorch vectors of dimensionality 100.

```{r}
# view embedded tokens.
for (token in seq_along(sentence)-1) {
  print(sentence[token])
  print(sentence[token]$embedding$numpy())
}
```


You choose which pre-trained embeddings you load by passing the appropriate id string to the constructor of the `WordEmbeddings` class. Typically, you use the **two-letter language code** to init an embedding, so 'en' for English and 'de' for German and so on. By default, this will initialize FastText embeddings trained over Wikipedia. You can also always use _FastText_ embeddings over Web crawls, by instantiating with '-crawl'. So 'de-crawl' to use embeddings trained over German web crawls.

For English, we provide a few more options, so here you can choose between instantiating '`en-glove`', '`en-extvec`' and so on.

### Suppored Models:

The following embeddings are currently supported:

| ID | Language | Embedding |
| ------------- | -------------  | ------------- |
| 'en-glove' (or 'glove') | English | GloVe embeddings |
| 'en-extvec' (or 'extvec') | English |Komninos embeddings |
| 'en-crawl' (or 'crawl')  | English | FastText embeddings over Web crawls |
| 'en-twitter' (or 'twitter')  | English | Twitter embeddings |
| 'en-turian' (or 'turian')  | English | Turian embeddings (small) |
| 'en' (or 'en-news' or 'news')  |English | FastText embeddings over news and wikipedia data |
| 'de' | German |German FastText embeddings |
| 'nl' | Dutch | Dutch FastText embeddings |
| 'fr' | French | French FastText embeddings |
| 'it' | Italian | Italian FastText embeddings |
| 'es' | Spanish | Spanish FastText embeddings |
| 'pt' | Portuguese | Portuguese FastText embeddings |
| 'ro' | Romanian | Romanian FastText embeddings |
| 'ca' | Catalan | Catalan FastText embeddings |
| 'sv' | Swedish | Swedish FastText embeddings |
| 'da' | Danish | Danish FastText embeddings |
| 'no' | Norwegian | Norwegian FastText embeddings |
| 'fi' | Finnish | Finnish FastText embeddings |
| 'pl' | Polish | Polish FastText embeddings |
| 'cz' | Czech | Czech FastText embeddings |
| 'sk' | Slovak | Slovak FastText embeddings |
| 'sl' | Slovenian | Slovenian FastText embeddings |
| 'sr' | Serbian | Serbian FastText embeddings |
| 'hr' | Croatian | Croatian FastText embeddings |
| 'bg' | Bulgarian | Bulgarian FastText embeddings |
| 'ru' | Russian | Russian FastText embeddings |
| 'ar' | Arabic | Arabic FastText embeddings |
| 'he' | Hebrew | Hebrew FastText embeddings |
| 'tr' | Turkish | Turkish FastText embeddings |
| 'fa' | Persian | Persian FastText embeddings |
| 'ja' | Japanese | Japanese FastText embeddings |
| 'ko' | Korean | Korean FastText embeddings |
| 'zh' | Chinese | Chinese FastText embeddings |
| 'hi' | Hindi | Hindi FastText embeddings |
| 'id' | Indonesian | Indonesian FastText embeddings |
| 'eu' | Basque | Basque FastText embeddings |

So, if you want to load German FastText embeddings, instantiate as follows:

```{r echo=FALSE}
german_embedding <- WordEmbeddings('de')
```


Alternatively, if you want to load German FastText embeddings trained over crawls, instantiate as follows:


```{r echo=FALSE}
german_embedding <- WordEmbeddings('de-crawl')
```



```{r echo=FALSE}
german_embedding <- WordEmbeddings('de-crawl')
```

</div>




&nbsp;

-----



# Embedding Examples

<div style="text-align: justify;">

Flair is a very popular natural language processing library, providing a variety of embedding methods for text representation. Flair Embeddings is a word embedding framework developed by [Zalando](https://engineering.zalando.com/posts/2018/11/zalando-research-releases-flair.html). It focuses on word-level representation and can capture contextual information of words, allowing the same word to have different embeddings in different contexts. Unlike traditional word embeddings (such as Word2Vec or GloVe), Flair can dynamically generate word embeddings based on context and has achieved excellent results in various NLP tasks. Below are some key points about Flair Embeddings:

</div>

**Context-Aware**

<div style="text-align: justify;">

Flair is a dynamic word embedding technique that can understand the meaning of words based on context. In contrast, static word embeddings, such as Word2Vec or GloVe, provide a fixed embedding for each word without considering its context in a sentence.

Therefore, context-sensitive embedding techniques, such as Flair, can capture the meaning of words in specific sentences more accurately, thus enhancing the performance of language models in various tasks.

</div>


__Example:__

<div style="text-align: justify;">

Consider the following two English sentences:

- "I am interested in the bank of the river."
- "I need to go to the bank to withdraw money."

Here, the word "bank" has two different meanings. In the first sentence, it refers to the edge or shore of a river. In the second sentence, it refers to a financial institution.

For static embeddings, the word "bank" might have an embedding that lies somewhere between these two meanings because it doesn't consider context. But for dynamic embeddings like Flair, "bank" in the first sentence will have an embedding related to rivers, and in the second sentence, it will have an embedding related to finance.

</div>


```{r}
# Initialize Flair embeddings
FlairEmbeddings <- flair_embeddings()$FlairEmbeddings
Sentence <- flair_data()$Sentence
flair_embedding_forward <- FlairEmbeddings('news-forward')

# Define the two sentences
sentence1 <-  Sentence("I am interested in the bank of the river.")
sentence2 <-  Sentence("I need to go to the bank to withdraw money.")

# Get the embeddings

flair_embedding_forward$embed(sentence1)
flair_embedding_forward$embed(sentence2)

# Extract the embedding for "bank" from the sentences
bank_embedding_sentence1 = sentence1[5]$embedding  # "bank" is the seventh word
bank_embedding_sentence2 = sentence2[6]$embedding  # "bank" is the sixth word
```

<div style="text-align: justify;">

Same word, similar vector representation, but essentially different. In this way, you can see how the dynamic embeddings for "bank" in the two sentences differ based on context. Although we printed the embeddings here, in reality, they would be high-dimensional vectors, so you might see a lot of numbers. If you want a more intuitive view of the differences, you could compute the cosine similarity or other metrics between the two embeddings.

This is just a simple demonstration. In practice, you can also combine multiple embedding techniques, such as `WordEmbeddings` and `FlairEmbeddings`, to get richer word vectors.

</div>

```{r}
library(lsa)
cosine(as.numeric( bank_embedding_sentence1$numpy()), 
       as.numeric( bank_embedding_sentence2$numpy()))
```

**Character-Based**

<div style="text-align: justify;">

Flair uses a character-level language model, meaning it can generate embeddings for rare words or even misspelled words. This is an important feature because it allows the model to understand and process words that have never appeared in the training data. Flair uses a bidirectional LSTM (Long Short-Term Memory) network that operates at a character level. This allows it to feed individual characters into the LSTM instead of words.

</div>

**Multilingual Support**

<div style="text-align: justify;">

Flair provides various pre-trained character-level language models, supporting contextual word embeddings for multiple languages. It allows you to easily combine different word embeddings (e.g., Flair Embeddings, Word2Vec, GloVe, etc.) to create powerful stacked embeddings.

</div>


## Classic Wordembeddings

<div style="text-align: justify;">

In Flair, the simplest form of embeddings that still contains semantic information about the word are called classic word embeddings. These embeddings are pre-trained and non-contextual.

Let's retrieve a few word embeddings and use FastText embeddings with the following code. To do so, we simply instantiate a WordEmbeddings class by passing in the ID of the embedding of our choice. Then, we simply wrap our text into a Sentence object, and call the `embed(sentence)` method on our WordEmbeddings class.

</div>


```{r}
WordEmbeddings <- flair_embeddings()$WordEmbeddings
Sentence <- flair_data()$Sentence
embedding <- WordEmbeddings('crawl')
sentence <- Sentence("one two three one") 
embedding$embed(sentence) 

for (i in seq_along(sentence$tokens)) {
  print(head(sentence$tokens[[i]]$embedding), n =5)
}

```

<div style="text-align: justify;">

Flair supports a range of classic word embeddings, each offering unique features and application scopes. Below is an overview, detailing the ID required to load each embedding and its corresponding language.

</div>

| Embedding Type              | ID      | Language   |
|-----------------------------|---------|------------|
| GloVe                       | glove   | English    |
| Komninos                    | extvec  | English    |
| Twitter                     | twitter | English    |
| Turian (small)              | turian  | English    |
| FastText (crawl)            | crawl   | English    |
| FastText (news & Wikipedia) | ar      | Arabic     |
| FastText (news & Wikipedia) | bg      | Bulgarian  |
| FastText (news & Wikipedia) | ca      | Catalan    |
| FastText (news & Wikipedia) | cz      | Czech      |
| FastText (news & Wikipedia) | da      | Danish     |
| FastText (news & Wikipedia) | de      | German     |
| FastText (news & Wikipedia) | es      | Spanish    |
| FastText (news & Wikipedia) | en      | English    |
| FastText (news & Wikipedia) | eu      | Basque     |
| FastText (news & Wikipedia) | fa      | Persian    |
| FastText (news & Wikipedia) | fi      | Finnish    |
| FastText (news & Wikipedia) | fr      | French     |
| FastText (news & Wikipedia) | he      | Hebrew     |
| FastText (news & Wikipedia) | hi      | Hindi      |
| FastText (news & Wikipedia) | hr      | Croatian   |
| FastText (news & Wikipedia) | id      | Indonesian |
| FastText (news & Wikipedia) | it      | Italian    |
| FastText (news & Wikipedia) | ja      | Japanese   |
| FastText (news & Wikipedia) | ko      | Korean     |
| FastText (news & Wikipedia) | nl      | Dutch      |
| FastText (news & Wikipedia) | no      | Norwegian  |
| FastText (news & Wikipedia) | pl      | Polish     |
| FastText (news & Wikipedia) | pt      | Portuguese |
| FastText (news & Wikipedia) | ro      | Romanian   |
| FastText (news & Wikipedia) | ru      | Russian    |
| FastText (news & Wikipedia) | si      | Slovenian  |
| FastText (news & Wikipedia) | sk      | Slovak     |
| FastText (news & Wikipedia) | sr      | Serbian    |
| FastText (news & Wikipedia) | sv      | Swedish    |
| FastText (news & Wikipedia) | tr      | Turkish    |
| FastText (news & Wikipedia) | zh      | Chinese    |



## Contexual Embeddings

<div style="text-align: justify;">

The idea behind contextual string embeddings is that each word embedding should be defined by not only its syntactic-semantic meaning but also the context it appears in. What this means is that each word will have a different embedding for every context it appears in. Each pre-trained Flair model offers a **forward** version and a **backward** version. Let's assume you are processing a language that, just like this text, uses the left-to-right script. The forward version takes into account the context that happens before the word -- on the left-hand side. The backward version works in the opposite direction. It takes into account the context after the word -- on the right-hand side of the word. If this is true, then two same words that appear at the beginning of two different sentences should have identical forward embeddings, because their context is null. Let's test this out:

Because we are using a forward model, it only takes into account the context that occurs before a word. Additionally, since our word has no context on the left-hand side of its position in the sentence, the two embeddings are identical, and the code assumes they are identical, indeed output is **True**.

</div>


```{r}
FlairEmbeddings <- flair_embeddings()$FlairEmbeddings
embedding <- FlairEmbeddings('news-forward')
s1 <- Sentence("nice shirt") 
s2 <- Sentence("nice pants") 

embedding$embed(s1) 
embedding$embed(s2) 
cat(" s1 sentence:", paste(s1[0], sep = ""), "\n", "s2 sentence:", paste(s2[0], sep = ""))
```

<div style="text-align: justify;">

We test whether the sum of the two 2048 embeddings of `nice` is equal to 2048. If it is true, it indicates that the embedding results are consistent, which should theoretically be the case.

</div>


```{r}
length(s1[0]$embedding$numpy()) == sum(s1[0]$embedding$numpy() ==  s2[0]$embedding$numpy())
```

Now we separately add a few more words, `very` and `pretty`, into two sentence objects.

```{r}
s1 <- Sentence("very nice shirt") 
s2 <- Sentence("pretty nice pants") 

embedding$embed(s1) 
embedding$embed(s2) 
```

The two sets of embeddings are not identical because the words are different, so it returns **FALSE**.

```{r}
length(s1[0]$embedding$numpy()) == sum(s1[0]$embedding$numpy() ==  s2[0]$embedding$numpy())
```

<div style="text-align: justify;">

The measure of similarity between two vectors in an inner product space is known as cosine similarity. The formula for calculating cosine similarity between two vectors, such as vectors A and B, is as follows:

$Cosine Similarity = \frac{\sum_{i} (A_i \cdot B_i)}{\sqrt{\sum_{i} (A_i^2)} \cdot \sqrt{\sum_{i} (B_i^2)}}$

</div>

```{r}
library(lsa)
vector1 <- as.numeric(s1[0]$embedding$numpy())
vector2 <- as.numeric(s2[0]$embedding$numpy())
```

We can observe that the similarity between the two words is 0.55.

```{r}
cosine_similarity <- cosine(vector1, vector2)
print(cosine_similarity)
```


------------------------------------------------------------------------

## Extracting Embeddings from BERT

<div style="text-align: justify;">

First, we utilize the `TransformerWordEmbeddings` function to download BERT, and more transformer models can also be found on [Flair NLP's Hugging Face](https://huggingface.co/flair).

</div>

```{r}
library(flaiR)
TransformerWordEmbeddings <- flair_embeddings()$TransformerWordEmbeddings("bert-base-uncased")
```

```{r}
embedding <- TransformerWordEmbeddings$embed(sentence)
```

Next, we traverse each token in the sentence and print them.

```{r}
# Iterate through each token in the sentence, printing them. 
# Utilize reticulate::py_str(token) to view each token, given that the sentence is a Python object.
for (i in seq_along(sentence$tokens)) {
  cat("Token: ", reticulate::py_str(sentence$tokens[[i]]), "\n")
  # Access the embedding of the token, converting it to an R object, 
  # and print the first 10 elements of the vector.
  token_embedding <- sentence$tokens[[i]]$embedding
  print(head(token_embedding, 10))
}
```


------------------------------------------------------------------------

## Visialized Embeddings


###  Word Embeddings (GloVe)

- GloVe embeddings are Pytorch vectors of dimensionality 100. 

- For English, Flair provides a few more options. Here, you can use `en-glove` and `en-extvec` with the __WordEmbeddings__ class.

```{r}
# Initialize Text Processing Tools ---------------------------
# Import Sentence class for text operations
Sentence <- flair_data()$Sentence

# Configure GloVe Embeddings --------------------------------
# Load WordEmbeddings class and initialize GloVe model
WordEmbeddings <- flair_embeddings()$WordEmbeddings
embedding <- WordEmbeddings("glove") 

# Text Processing and Embedding -----------------------------
# Create sentence with semantic relationship pairs
sentence <- Sentence("King Queen man woman Paris London apple orange Taiwan Dublin Bamberg") 

# Apply GloVe embeddings to the sentence
embedding$embed(sentence)

# Extract embeddings into matrix format
sen_df <- process_embeddings(sentence, 
                          verbose = TRUE)

# Dimensionality Reduction ---------------------------------
# Set random seed for reproducibility
set.seed(123)

# Apply PCA to reduce dimensions to 3 components
pca_result <- prcomp(sen_df, center = TRUE, scale. = TRUE)

# Extract first three principal components
word_embeddings_matrix <- as.data.frame(pca_result$x[,1:3])
word_embeddings_matrix
```

#### 2D Plot

```{r,  out.width="95%" }
library(ggplot2)
glove_plot2D <- ggplot(word_embeddings_matrix, aes(x = PC1, y = PC2, color = PC3, 
                                             label = rownames(word_embeddings_matrix))) +
  geom_point(size = 3) + 
  geom_text(vjust = 1.5, hjust = 0.5) +  
  scale_color_gradient(low = "blue", high = "red") + 
  theme_minimal() +  
  labs(title = "", x = "PC1", y = "PC2", color = "PC3") 
  # guides(color = "none")  
glove_plot2D
```

#### 3D Plot

[plotly](https://plotly.com/r/) in R API: https://plotly.com/r/

```{r, message = FALSE, warning = FALSE, out.width="95%"}
library(plotly)
glove_plot3D <- plot_ly(data = word_embeddings_matrix, 
                  x = ~PC1, y = ~PC2, z = ~PC3, 
                  type = "scatter3d", mode = "markers",
                  marker = list(size = 5), 
                  text = rownames(word_embeddings_matrix), hoverinfo = 'text')

glove_plot3D
```

### Stack Embeddings Method (GloVe + Back/forwad FlairEmbeddings or More)

```{r}
# Initialize Embeddings -----------------------------
# Load embedding types from flaiR
WordEmbeddings <- flair_embeddings()$WordEmbeddings
FlairEmbeddings <- flair_embeddings()$FlairEmbeddings
StackedEmbeddings <- flair_embeddings()$StackedEmbeddings

# Configure Embeddings ----------------------------
# Initialize GloVe word embeddings
glove_embedding <- WordEmbeddings('glove')

# Initialize Flair contextual embeddings
flair_embedding_forward <- FlairEmbeddings('news-forward')
flair_embedding_backward <- FlairEmbeddings('news-backward')

# Initialize GloVe for individual use
embedding <- WordEmbeddings("glove") 

# Create stacked embeddings combining GloVe and bidirectional Flair
stacked_embeddings <- StackedEmbeddings(c(glove_embedding,
                                         flair_embedding_forward,
                                         flair_embedding_backward))

# Text Processing --------------------------------
# Load Sentence class from flaiR
Sentence <- flair_data()$Sentence

# Create test sentence with semantic relationships
sentence <- Sentence("King Queen man woman Paris London apple orange Taiwan Dublin Bamberg") 

# Apply embeddings and extract features ----------
# Embed text using stacked embeddings
stacked_embeddings$embed(sentence)

# Extract embeddings matrix with processing details
sen_df <- process_embeddings(sentence, 
                           verbose = TRUE)

# Dimensionality Reduction -----------------------
set.seed(123)

# Perform PCA for visualization
pca_result <- prcomp(sen_df, center = TRUE, scale. = TRUE)

# Extract first three principal components
word_embeddings_matrix <- as.data.frame(pca_result$x[,1:3])
word_embeddings_matrix
```

```{r,  out.width="95%" }
# 2D Plot
library(ggplot2)

stacked_plot2D <- ggplot(word_embeddings_matrix, aes(x = PC1, y = PC2, color = PC3, 
                                             label = rownames(word_embeddings_matrix))) +
  geom_point(size = 2) + 
  geom_text(vjust = 1.5, hjust = 0.5) +  
  scale_color_gradient(low = "blue", high = "red") + 
  theme_minimal() +  
  labs(title = "", x = "PC1", y = "PC2", color = "PC3") 

stacked_plot2D
```


### Transformer Embeddings (BERT or More)

```{r}
# Load Required Package ----------------------------
library(flaiR)

# Initialize BERT and Text Processing --------------
# Import Sentence class for text operations
Sentence <- flair_data()$Sentence

# Initialize BERT model (base uncased version)
TransformerWordEmbeddings <- flair_embeddings()$TransformerWordEmbeddings("bert-base-uncased")

# Text Processing and Embedding --------------------
# Create sentence with semantic relationship pairs
sentence <- Sentence("King Queen man woman Paris London apple orange Taiwan Dublin Bamberg") 

# Apply BERT embeddings to the sentence
TransformerWordEmbeddings$embed(sentence)

# Extract embeddings into matrix format
sen_df <- process_embeddings(sentence, verbose = TRUE)

# Dimensionality Reduction ------------------------
# Set random seed for reproducibility
set.seed(123)

# Apply PCA to reduce dimensions to 3 components
pca_result <- prcomp(sen_df, center = TRUE, scale. = TRUE)

# Extract first three principal components
word_embeddings_matrix <- as.data.frame(pca_result$x[,1:3])
word_embeddings_matrix
```

```{r,  out.width="95%" }
# 2D Plot
library(ggplot2)

bert_plot2D <- ggplot(word_embeddings_matrix, aes(x = PC1, y = PC2, color = PC3, 
                                             label = rownames(word_embeddings_matrix))) +
  geom_point(size = 2) + 
  geom_text(vjust = 1.5, hjust = 0.5) +  
  scale_color_gradient(low = "blue", high = "red") + 
  theme_minimal() +  
  labs(title = "", x = "PC1", y = "PC2", color = "PC3") 
  # guides(color = "none") 

stacked_plot2D
```

### Embedding Models Comparison
```{r,  out.width="95%" }
library(ggpubr)

figure <- ggarrange(glove_plot2D, stacked_plot2D, bert_plot2D,
                   labels = c("Glove", "Stacked Embedding", "BERT"),
                   ncol = 3, nrow = 1,
                   common.legend = TRUE,
                   legend = "bottom",
                   font.label = list(size = 8))

figure
```


&nbsp;

-----


# Training a Binary Classifier

In this section, we'll train a sentiment analysis model that can categorize text as either positive or negative. This case study is adapted from pages 116 to 130 of Tadej Magajna's book, '[Natural Language Processing with Flair](https://www.packtpub.com/product/natural-language-processing-with-flair/9781801072311)'. The process for training text classifiers in Flair mirrors the process followed for sequence labeling models. Specifically, the steps to train text classifiers are:

- Load a tagged corpus and compute the label dictionary map.
- Prepare the document embeddings.
- Initialize the `TextClassifier` class.
- Train the model.

## Loading a Tagged Corpus

<div style="text-align: justify;">

Training text classification models requires a set of text documents (typically, sentences or paragraphs) where each document is associated with one or more classification labels. To train our sentiment analysis text classification model, we will be using the famous Internet Movie Database (IMDb) dataset, which contains 50,000 movie reviews from IMDB, where each review is labeled as either positive or negative. References to this dataset are already baked into Flair, so loading the dataset couldn't be easier:

</div>

```{r}
library(flaiR)
# load IMDB from flair_datasets module
Corpus <- flair_data()$Corpus
IMDB <- flair_datasets()$IMDB
```

```{r}
# downsize to 0.05
corpus = IMDB()
corpus$downsample(0.05)
```

Print the sizes in the corpus object as follows - test: %d \| train: %d \| dev: %d"

```{r}
test_size <- length(corpus$test)
train_size <- length(corpus$train)
dev_size <- length(corpus$dev)
output <- sprintf("Corpus object sizes - Test: %d | Train: %d | Dev: %d", test_size, train_size, dev_size)
print(output)
```

```{r}
lbl_type = 'sentiment'
label_dict = corpus$make_label_dictionary(label_type=lbl_type)
```


## Loading the Embeddings

<div style="text-align: justify;">

flaiR covers all the different types of document embeddings that we can use. Here, we simply use `DocumentPoolEmbeddings`. They require no training prior to training the classification model itself:

</div>

```{r}
DocumentPoolEmbeddings <- flair_embeddings()$DocumentPoolEmbeddings
WordEmbeddings <- flair_embeddings()$WordEmbeddings
glove = WordEmbeddings('glove')
document_embeddings = DocumentPoolEmbeddings(glove)
```

## Initializing the TextClassifier

```{r}
# initiate TextClassifier
TextClassifier <- flair_models()$TextClassifier
classifier <- TextClassifier(document_embeddings,
                             label_dictionary = label_dict,
                             label_type = lbl_type)
```


`$to` allows you to set the device to use CPU, GPU, or specific MPS devices on Mac (such as mps:0, mps:1, mps:2).


```{r eval=FALSE, include=TRUE}
classifier$to(flair_device("mps")) 
```

```         
TextClassifier(
  (embeddings): DocumentPoolEmbeddings(
    fine_tune_mode=none, pooling=mean
    (embeddings): StackedEmbeddings(
      (list_embedding_0): WordEmbeddings(
        'glove'
        (embedding): Embedding(400001, 100)
      )
    )
  )
  (decoder): Linear(in_features=100, out_features=3, bias=True)
  (dropout): Dropout(p=0.0, inplace=False)
  (locked_dropout): LockedDropout(p=0.0)
  (word_dropout): WordDropout(p=0.0)
  (loss_function): CrossEntropyLoss()
)
```


## Training the Model


Training the text classifier model involves two simple steps:

- Defining the model trainer class by passing in the classifier model and the corpus
- Setting off the training process passing in the required training hyper-parameters.


<div style="text-align: justify;">

**It is worth noting that the 'L' in numbers like 32L and 5L is used in R to denote that the number is an integer. Without the 'L' suffix, numbers in R are treated as numeric, which are by default double-precision floating-point numbers. In contrast, Python determines the type based on the value of the number itself. Whole numbers (e.g., 5 or 32) are of type int, while numbers with decimal points (e.g., 5.0) are of type float. Floating-point numbers in both languages are representations of real numbers but can have some approximation due to the way they are stored in memory.**

</div>


```{r}
# initiate ModelTrainer
ModelTrainer <- flair_trainers()$ModelTrainer

# fit the model
trainer <- ModelTrainer(classifier, corpus)

# start to train
# note: the 'L' in 32L is used in R to denote that the number is an integer.
trainer$train('classifier',
              learning_rate=0.1,
              mini_batch_size=32L,
              # specifies how embeddings are stored in RAM, ie."cpu", "cuda", "gpu", "mps".
              # embeddings_storage_mode = "mps",
              max_epochs=10L)
```



## Loading and Using the Classifiers

<div style="text-align: justify;">

After training the text classification model, the resulting classifier will already be stored in memory as part of the classifier variable. It is possible, however, that your Python session exited after training. If so, you'll need to load the model into memory with the following:

</div>

```{r}
TextClassifier <- flair_models()$TextClassifier
classifier <- TextClassifier$load('classifier/best-model.pt')
```

We import the Sentence object. Now, we can generate predictions on some example text inputs.

```{r}
Sentence <- flair_data()$Sentence
```

```{r}
sentence <- Sentence("great")
classifier$predict(sentence)
print(sentence$labels)
```

```{r}
sentence <- Sentence("sad")
classifier$predict(sentence)
print(sentence$labels)
```


&nbsp;

-----


# Training RNNs

<div style="text-align: justify;">

Here, we train a sentiment analysis model to categorize text. In this case, we also include a pipeline that implements the use of Recurrent Neural Networks (RNN). This makes them particularly effective for tasks involving sequential data. This section also show you how to implement one of most powerful features in flaiR, stacked embeddings. You can stack multiple embeddings with different layers and let the classifier learn from different types of features. In Flair NLP, and with the **flaiR** package, it's very easy to accomplish this task.

</div>

## Import Necessary Modules

```{r}
library(flaiR)
WordEmbeddings <- flair_embeddings()$WordEmbeddings
FlairEmbeddings <- flair_embeddings()$FlairEmbeddings
DocumentRNNEmbeddings <- flair_embeddings()$DocumentRNNEmbeddings
TextClassifier <- flair_models()$TextClassifier
ModelTrainer <- flair_trainers()$ModelTrainer
```


## Get the IMDB Corpus

<div style="text-align: justify;">

The IMDB movie review dataset is used here, which is a commonly utilized dataset for sentiment analysis. `$downsample(0.1)` method means only 10% of the dataset is used, allowing for a faster demonstration.

</div>


```{r}
# load the IMDB file and downsize it to 0.1
IMDB <- flair_datasets()$IMDB
corpus <- IMDB()$downsample(0.1) 
# create the label dictionary
lbl_type <- 'sentiment'
label_dict <- corpus$make_label_dictionary(label_type=lbl_type)
```

## Stacked Embeddings

<div style="text-align: justify;">

This is one of Flair's most powerful features: it allows for the integration of embeddings to enable the model to learn from more sparse features. Three types of embeddings are utilized here: GloVe embeddings, and two types of Flair embeddings (forward and backward). Word embeddings are used to convert words into vectors.

</div>


```{r}
# make a list of word embeddings
word_embeddings <- list(WordEmbeddings('glove'),
                        FlairEmbeddings('news-forward-fast'),
                        FlairEmbeddings('news-backward-fast'))

# initialize the document embeddings
document_embeddings <- DocumentRNNEmbeddings(word_embeddings, 
                                             hidden_size = 512L,
                                             reproject_words = TRUE,
                                             reproject_words_dimension = 256L)
```

```{r}
# create a Text Classifier with the embeddings and label dictionary
classifier <- TextClassifier(document_embeddings, 
                            label_dictionary=label_dict, label_type='class')

# initialize the text classifier trainer with our corpus
trainer <- ModelTrainer(classifier, corpus)
```

## Start the Training

<div style="text-align: justify;">

For the sake of this example, setting max_epochs to 5. You might want to increase this for better performance.

It is worth noting that the learning rate is a parameter that determines the step size at each iteration while moving towards a minimum of the loss function. A smaller learning rate could slow down the learning process, but it could lead to more precise convergence. `mini_batch_size` determines the number of samples that will be used to compute the gradient at each step. The 'L' in 32L is used in R to denote that the number is an integer.

`patience` (aka early stop) is a hyper-parameter used in conjunction with early stopping to avoid overfitting. It determines the number of epochs the training process will tolerate without improvements before stopping the training. Setting max_epochs to 5 means the algorithm will make five passes through the dataset.

</div>


```{r eval=FALSE, include=TRUE}
# note: the 'L' in 32L is used in R to denote that the number is an integer.
trainer$train('models/sentiment',
              learning_rate=0.1,
              mini_batch_size=32L,
              patience=5L,
              max_epochs=5L)  
```

## To Apply the Trained Model for Prediction

```{r eval=FALSE, include=TRUE}
sentence <- "This movie was really exciting!"
classifier$predict(sentence)
print(sentence.labels)
```

------------------------------------------------------------------------

# Finetune Transformers

<div style="text-align: justify;">

We use data from *The Temporal Focus of Campaign Communication (2020 JOP)* as an example. Let's assume we receive the data for training from different times. First, suppose you have a dataset of 1000 entries called `cc_muller_old`. On another day, with the help of nice friends, you receive another set of data, adding 2000 entries in a dataset called `cc_muller_new`. Both subsets are from `data(cc_muller)`. We will show how to fine-tune a transformer model with `cc_muller_old`, and then continue with another round of fine-tuning using `cc_muller_new`.

</div>

```{r}
library(flaiR)
```


## Fine-tuning a Transformers Model

<u>**Step 1**</u> Load Necessary Modules from Flair

Load necessary classes from `flair` package.

```{r}
# Sentence is a class for holding a text sentence
Sentence <- flair_data()$Sentence

# Corpus is a class for text corpora
Corpus <- flair_data()$Corpus

# TransformerDocumentEmbeddings is a class for loading transformer 
TransformerDocumentEmbeddings <- flair_embeddings()$TransformerDocumentEmbeddings

# TextClassifier is a class for text classification
TextClassifier <- flair_models()$TextClassifier

# ModelTrainer is a class for training and evaluating models
ModelTrainer <- flair_trainers()$ModelTrainer
```

<div style="text-align: justify;">

We use purrr to help us split sentences using Sentence from `flair_data()`, then use map2 to add labels, and finally use `Corpus` to segment the data.

</div>


```{r}
library(purrr)

data(cc_muller)
cc_muller_old <- cc_muller[1:1000,]

old_text <- map(cc_muller_old$text, Sentence)
old_labels <- as.character(cc_muller_old$class)

old_text <- map2(old_text, old_labels, ~ {
  .x$add_label("classification", .y)
  .x
})
```

```{r}
print(length(old_text))
```

```{r}
set.seed(2046)
sample <- sample(c(TRUE, FALSE), length(old_text), replace=TRUE, prob=c(0.8, 0.2))
old_train  <- old_text[sample]
old_test   <- old_text[!sample]

test_id <- sample(c(TRUE, FALSE), length(old_test), replace=TRUE, prob=c(0.5, 0.5))
old_test   <- old_test[test_id]
old_dev   <- old_test[!test_id]
```

<div style="text-align: justify;">

If you do not provide a development set (dev set) while using Flair, it will automatically split the training data into training and development datasets. The test set is used for training the model and evaluating its final performance, whereas the development set is used for adjusting model parameters and preventing overfitting, or in other words, for early stopping of the model.

</div>

```{r}
old_corpus <- Corpus(train = old_train, test = old_test)
```

<u>**Step 3**</u> Load `distilbert` Transformer

```{r}
document_embeddings <- TransformerDocumentEmbeddings('distilbert-base-uncased', fine_tune=TRUE)
```

<div style="text-align: justify;">

First, the `$make_label_dictionary` function is used to automatically create a label dictionary for the classification task. The label dictionary is a mapping from label to index, which is used to map the labels to a tensor of label indices. Besides classification tasks, flaiR also supports other label types for training custom model. From the cc_muller dataset: Future (seen 423 times), Present (seen 262 times), Past (seen 131 times).

</div>


```{r}
old_label_dict <- old_corpus$make_label_dictionary(label_type="classification")
```

<div style="text-align: justify;">

`TextClassifier` is used to create a text classifier. The classifier takes the document embeddings (importing from `'distilbert-base-uncased'` from Hugging Face) and the label dictionary as input. The label type is also specified as classification.

</div>

```{r}
old_classifier <- TextClassifier(document_embeddings,
                                 label_dictionary = old_label_dict, 
                                 label_type='classification')
```

<u>**Step 4**</u> Start Training

`ModelTrainer` is used to train the model.

```{r eval=TRUE}
old_trainer <- ModelTrainer(model = old_classifier, corpus = old_corpus)
```

```{r eval=TRUE}
old_trainer$train("vignettes/inst/muller-campaign-communication",  
                  learning_rate=0.02,              
                  mini_batch_size=8L,              
                  anneal_with_restarts = TRUE,
                  save_final_model=TRUE,
                  max_epochs=1L)   
```


## Continue Fine-tuning with New Dataset

<div style="text-align: justify;">

Now, we can continue to fine tune the already fine tuned model with an additional 2000 pieces of data. First, let's say we have another 2000 entries called `cc_muller_new`. We can fine-tune the previous model with these 2000 entries. The steps are the same as before. For this case, we don't need to split the dataset again. We can use the entire 2000 entries as the training set and use the `old_test` set to evaluate how well our refined model performs.

</div>

<u>**Step 1**</u> Load the `muller-campaign-communication` Model


Load the model (`old_model`) you have already fine tuned from previous stage and let's fine tune it with the new data, `new_corpus`.


```{r}
old_model <- TextClassifier$load("vignettes/inst/muller-campaign-communication/best-model.pt")
```

<u>**Step 2**</u> Convert the New Data to Sentence and Corpus

```{r}
library(purrr)
cc_muller_new <- cc_muller[1001:3000,]
new_text <- map(cc_muller_new$text, Sentence)
new_labels <- as.character(cc_muller_new$class)

new_text <- map2(new_text, new_labels, ~ {
  .x$add_label("classification", .y)
  .x
})
```

```{r}
new_corpus <- Corpus(train=new_text, test=old_test)
```

<u>**Step 3**</u> Create a New Model Trainer with the Old Model and New Corpus

```{r}
new_trainer <- ModelTrainer(old_model, new_corpus)
```

<u>**Step 4**</u> Train the New Model

```{r eval=TRUE}
new_trainer$train("vignettes/inst/new-muller-campaign-communication",
                  learning_rate=0.002, 
                  mini_batch_size=8L,  
                  max_epochs=1L)    
```


## Model Performance Metrics: Pre and Post Fine-tuning


After fine-tuning for 1 epoch, the model showed improved performance on the same test set.


| Evaluation Metric | Pre-finetune | Post-finetune | Improvement |
|-------------------|--------------|---------------|-------------|
| F-score (micro)   | 0.7294       | 0.8471        | +0.1177     |
| F-score (macro)   | 0.7689       | 0.8583        | +0.0894     |
| Accuracy          | 0.7294       | 0.8471        | +0.1177     |

More R tutorial and documentation see [here](https://github.com/davidycliao/flaiR).

## Using Your Own Fine-tuned Model in flaiR

This seciton demonstrates how to utilize your custom fine-tuned model in flaiR for text classification tasks. Let's explore this process step by step.

<u>**Setting Up Your Environment**</u> 

First, we need to load the flaiR package and prepare our model:


```{r}
library(flaiR)
classifier <- flair_models()$TextClassifier$load('vignettes/inst/new-muller-campaign-communication/best-model.pt')
```

It's important to verify your model's compatibility with `$model_card`. You can check this by examining the version requirements:

```{r}
print(classifier$model_card)
```

```{r}
# Check required versions
print(classifier$model_card$transformers_version)  # Required transformers version
print(classifier$model_card$flair_version)         # Required Flair version
```

<u>**Making Predictions**</u> 

To make predictions, we first need to prepare our text by creating a Sentence object. This is a key component in Flair's architecture that handles text processing:

```{r}
# Get the Sentence class from flaiR
Sentence <- flair_data()$Sentence

# Create a Sentence object with your text
sentence <- Sentence("And to boost the housing we need, we will start to build a new generation of garden cities.")

# Make prediction
classifier$predict(sentence)

```

<u>**Access Prediction Results**</u> 

Get predicted label
```{r}
prediction <- sentence$labels[[1]]$value
print(prediction)
```

Get confidence score
```{r}
confidence <- sentence$labels[[1]]$score 
print(confidence)
```


&nbsp;

-----


# Extending conText's Embedding Regression

<div style="text-align: justify;">

`ConText` is a fast, flexible, and transparent framework for estimating context-specific word and short document embeddings using [the 'a la carte' embeddings regression](https://github.com/prodriguezsosa/EmbeddingRegression), implemented by [Rodriguez et al (2022)](https://www.cambridge.org/core/journals/american-political-science-review/article/embedding-regression-models-for-contextspecific-description-and-inference/4C90013E5C714C8483ED95CC699022FB) and [Rodriguez et al (2024)](https://www.cambridge.org/core/journals/political-analysis/article/multilanguage-word-embeddings-for-social-scientists-estimation-inference-and-validation-resources-for-157-languages/F5DE16FA784CA81481150715967BD9FC).

In this case study, we will demonstrate how to use the conText package alongside other embedding frameworks by working through the example provided in Rodriguez et al.'s [Quick Start Guide](https://github.com/prodriguezsosa/conText/blob/master/vignettes/quickstart.md). While ConText includes its own cross-lingual ALC Embeddings, this tutorial extends its capabilities by integrating it with flaiR. Through this tutorial integration, this tutorial shows how to:

</div>


- Access flaiR's powerful embedding models

- Connect with any transformer-based embedding models from HuggingFace via FlaiR


<div style="text-align: justify;">

We will be following the example directly from [Rodriguez et al.'s Quick Start Guide]() as this case study. It's important to note that results obtained using alternative embedding frameworks may deviate from the original implementation, and should be interpreted with caution. These comparative results are primarily intended for reference and educational use.

First of all, when loading the conText package, you'll find three pre-loaded datasets: `cr_sample_corpus`, `cr_glove_subset`, and `cr_transform.` These datasets are used in the package's tutorial to demonstrate preprocessing steps. For this exercise, we only use `cr_sample_corpus` to explore other embedding frameworks, including:

</div>


- `en-crawl` embedding
- Flair NLP contextual embeddings (as described in  [Akbik et al., COLING 2018 paper](https://flairnlp.github.io/docs/tutorial-embeddings/flair-embeddings))

- Integrated embeddings extracted from transformers like BERT.


## Build Document-Embedding-Matrix with Other Embedding Frameworks

```{r warning=FALSE, include=FALSE}
remotes::install_github("prodriguezsosa/conText", force = TRUE)
library(conText)
library(quanteda)
library(dplyr)
library(flaiR)
```

<u>**Step 1**</u> Tokenize Text with `quanteda` and `conText`


First, let's tokenize `cr_sample_corpus` using the tokens_context function from the conText package.

```{r}
# tokenize corpus removing unnecessary (i.e. semantically uninformative) elements
toks <- tokens(cr_sample_corpus, 
               remove_punct = TRUE, 
               remove_symbols = TRUE, 
               remove_numbers = TRUE,
               remove_separators  = TRUE)

# clean out stopwords and words with 2 or fewer characters
toks_nostop <- tokens_select(toks, 
                             pattern = stopwords("en"), 
                             selection = "remove", 
                             min_nchar=3)

# only use features that appear at least 5 times in the corpus
feats <- dfm(toks_nostop, tolower = TRUE, verbose = FALSE) %>% 
  dfm_trim(min_termfreq = 5) %>% featnames()

# leave the pads so that non-adjacent words will not become adjacent
toks_nostop_feats <- tokens_select(toks_nostop, feats, padding = TRUE)

# build a tokenized corpus of contexts surrounding the target term "immigration"
immig_toks <- tokens_context(x = toks_nostop_feats, pattern = "immigr*", window = 6L)

# build document-feature matrix
immig_dfm <- dfm(immig_toks)
```

<u>**Step 2**</u> Import Embedding Tools

<div style="text-align: justify;">

To facilitate the loading of different embedding types, I'll import the following __classes__ and __functions__ from flaiR: `WordEmbeddings`, `FlairEmbeddings`, `TransformerWordEmbeddings`, `StackedEmbeddings`, and `Sentence.` These components enable us to work with GloVe embeddings, Flair's contextual embeddings, and transformer-based embeddings from the HuggingFace library.

</div>

```{r include=FALSE}
# Load the flaiR library
library(flaiR)

# Import embedding classes from flair
WordEmbeddings <- flair_embeddings()$WordEmbeddings 

# Import Sentence class for text processing
Sentence <- flair_data()$Sentence

# Initialize FastText embeddings trained on Common Crawl
fasttext_embeddings <- WordEmbeddings('en-news')
```

<div style="text-align: justify;">

Initialize a Flair Sentence object by concatenating cr_glove_subset row names. The collapse parameter ensures proper tokenization by adding space delimiters. Then, embed the sentence text using the loaded fasttext embeddings.

</div>

```{r}
# Combine all text into a single string and create a Flair sentence
sentence <- Sentence(paste(rownames(cr_glove_subset), collapse = " "))

# Apply FastText embeddings to the sentence
fasttext_embeddings$embed(sentence)
```

<div style="text-align: justify;">

The `process_embeddings` function from flaiR extracts pre-embedded GloVe vectors from a sentence object and arranges them into a structured matrix. In this matrix, tokens are represented as rows, embedding dimensions as columns, and each row is labeled with its corresponding token text.

</div>

```{r}
fasttext_subset <- process_embeddings(sentence, verbose = TRUE)
```

<u>**Step 3**</u> Computing Context-Specific Word Embeddings Using FastText

<div style="text-align: justify;">

Create a feature co-occurrence matrix (FCM) from tokenized text and transform pre-trained FastText embeddings using co-occurrence information.

</div>

```{r}
# Create a feature co-occurrence matrix (FCM) from tokenized text
toks_fcm <- fcm(toks_nostop_feats, 
                context = "window",    
                window = 6,            
                count = "frequency",   
                tri = FALSE)           

# Transform pre-trained Glove embeddings using co-occurrence information
ft_transform <- compute_transform(
    x = toks_fcm,                    
    pre_trained = fasttext_subset,        
    weighting = 'log'                
)
```

Calculate Document Embedding Matrix (DEM) using transformed FastText embeddings.

```{r}
# Calculate Document Embedding Matrix (DEM) using transformed FastText embeddings
immig_dem_ft <- dem(x = immig_dfm, 
                    pre_trained = fasttext_subset, 
                    transform = TRUE, 
                    transform_matrix = ft_transform, 
                    verbose = TRUE)
```

Show each document inherits its corresponding docvars.

```{r}
head(immig_dem_ft@docvars)
```


<u>**Step 4**</u> Embedding Regression

```{r}
set.seed(2021L)
library(conText)
ft_model <- conText(formula = immigration ~ party + gender,
                    data = toks_nostop_feats,
                    pre_trained = fasttext_subset,
                    transform = TRUE,
                    transform_matrix = ft_transform,
                    confidence_level = 0.95,
                    permute = FALSE,
                    jackknife = FALSE,
                    num_permutations = 100,
                    window = 6,
                    case_insensitive = TRUE,
                    verbose = FALSE)
```

extract D-dimensional beta coefficients. 

```{r}
# The intercept in this case is the fastext embedding for female Democrats
# beta coefficients can be combined to get each group's fastext embedding
DF_wv <- ft_model['(Intercept)',]  # (D)emocrat - (F)emale 
DM_wv <- ft_model['(Intercept)',] + ft_model['gender_M',] # (D)emocrat - (M)ale 
RF_wv <- ft_model['(Intercept)',] + ft_model['party_R',]  # (R)epublican - (F)emale 
RM_wv <- ft_model['(Intercept)',] + ft_model['party_R',] + ft_model['gender_M',] # (R)epublican - (M)ale
```

nearest neighbors


```{r}
nns(rbind(DF_wv,DM_wv), 
    N = 10, 
    pre_trained = fasttext_subset, 
    candidates = ft_model@features)
```


```{r}
nns(rbind(RF_wv,RM_wv), 
    N = 10, 
    pre_trained = fasttext_subset, 
    candidates = ft_model@features)
```

## Exploring Document-Embedding Matrix with conText Functions

Check dimensions of the resulting matrix.
```{r}
# Calculate average document embeddings for immigration-related texts
immig_wv_ft <- matrix(colMeans(immig_dem_ft), 
                   ncol = ncol(immig_dem_ft)) %>%  `rownames<-`("immigration")
dim(immig_wv_ft)
```

to get group-specific embeddings, average within party
```{r}
immig_wv_ft_party <- dem_group(immig_dem_ft, 
                               groups = immig_dem_ft@docvars$party)
dim(immig_wv_ft_party)
```

Find nearest neighbors by party
```{r}
# find nearest neighbors by party
# setting as_list = FALSE combines each group's results into a single tibble (useful for joint plotting)
immig_nns_ft <- nns(immig_wv_ft_party, 
                    pre_trained = fasttext_subset, 
                    N = 5, 
                    candidates = immig_wv_ft_party@features, 
                    as_list = TRUE)
```

check out results for Republican.
```{r}
immig_nns_ft[["R"]]
```

check out results for Democrat
```{r}
immig_nns_ft[["D"]]
```

compute the cosine similarity between each party's embedding and a specific set of features
```{r}
cos_sim(immig_wv_ft_party, 
        pre_trained = fasttext_subset, 
        features = c('reform', 'enforcement'), as_list = FALSE)
```

compute the cosine similarity between each party's embedding and a specific set of features.

```{r}
# Republican
nns_ratio(x = immig_wv_ft_party, 
          N = 15, 
          numerator = "R", 
          candidates = immig_wv_ft_party@features, 
          pre_trained = fasttext_subset, 
          verbose = FALSE)
```

```{r}
# Democrat
nns_ratio(x = immig_wv_ft_party, 
          N = 15, 
          numerator = "D", 
          candidates = immig_wv_ft_party@features, 
          pre_trained = fasttext_subset, 
          verbose = FALSE)
```

compute the cosine similarity between each party's embedding and a set of tokenized contexts
```{r}
immig_ncs <- ncs(x = immig_wv_ft_party, 
                 contexts_dem = immig_dem_ft, 
                 contexts = immig_toks, 
                 N = 5, 
                 as_list = TRUE)

# nearest contexts to Republican embedding of target term
# note, these may included contexts originating from Democrat speakers
immig_ncs[["R"]]
```

```{r}
immig_ncs[["D"]]
```

<!-- ## Comparative Analysis of A La Carte, Flair Stacked, and BERT Embeddings -->

<!-- ### Build A La Carte Document-Embedding-Matrix   -->

<!-- ```{r} -->
<!-- # build a document-embedding-matrix -->
<!-- immig_dem <- dem(x = immig_dfm, pre_trained = cr_glove_subset, transform = TRUE, transform_matrix = cr_transform, verbose = TRUE) -->

<!-- set.seed(2021L) -->
<!-- alc_model <- conText(formula = immigration ~ party + gender, -->
<!--                      data = toks_nostop_feats, -->
<!--                      pre_trained = cr_glove_subset, -->
<!--                      transform = TRUE,  -->
<!--                      transform_matrix = cr_transform, -->
<!--                      jackknife = TRUE,  -->
<!--                      confidence_level = 0.95, -->
<!--                      permute = TRUE,  -->
<!--                      num_permutations = 100, -->
<!--                      window = 6,  -->
<!--                      case_insensitive = TRUE, -->
<!--                      verbose = FALSE) -->
<!-- ``` -->

<!-- ### Document Embedding Matrix Construction Using Flair Contextual Stacked Embeddings -->

<!-- <div style="text-align: justify;"> -->

<!-- To facilitate the loading of different embedding types, I'll import the following __classes__ and __functions__ from flaiF: `WordEmbeddings`, `FlairEmbeddings`, `TransformerWordEmbeddings`, `StackedEmbeddings`, and `Sentence`. These components enable us to work with GloVe embeddings, Flair's contextual embeddings, and transformer-based embeddings from the HuggingFace library. -->

<!-- </div> -->

<!-- ```{r include=FALSE} -->
<!-- # Load the flaiR library -->
<!-- library(flaiR) -->

<!-- # Import embedding classes from flair -->
<!-- WordEmbeddings <- flair_embeddings()$WordEmbeddings  -->
<!-- FlairEmbeddings <- flair_embeddings()$FlairEmbeddings -->
<!-- TransformerWordEmbeddings <- flair_embeddings()$TransformerWordEmbeddings -->
<!-- StackedEmbeddings <- flair_embeddings()$StackedEmbeddings -->

<!-- # Import Sentence class for text processing -->
<!-- Sentence <- flair_data()$Sentence -->

<!-- # Initialize FastText embeddings trained on Common Crawl -->
<!-- fasttext_embeddings <- WordEmbeddings('en-crawl') -->

<!-- # Initialize Flair's forward language model embeddings trained on news data -->
<!-- flair_forward <- FlairEmbeddings('news-forward') -->

<!-- # Initialize Flair's backward language model embeddings trained on news data   -->
<!-- flair_backward <- FlairEmbeddings('news-backward') -->

<!-- ``` -->

<!-- Combine three different types of embeddings into a stacked embedding model. -->

<!-- This creates a stacked embedding model that combines: -->

<!-- - `FastText embeddings`: Captures general word semantics -->
<!-- - `Forward Flair`: Captures contextual information reading text left-to-right -->
<!-- - `Backward Flair`: Captures contextual information reading text right-to-left -->


<!-- ```{r} -->
<!-- stacked_embeddings  <- StackedEmbeddings(list( -->
<!--   fasttext_embeddings,     -->
<!--   flair_forward,           -->
<!--   flair_backward         -->
<!-- )) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # Step 1: Create a Flair Sentence object from the text -->
<!-- sentence <- Sentence(paste(rownames(cr_glove_subset), collapse = " ")) -->

<!-- # Step 2: Generate embeddings using our stacked model -->
<!-- stacked_embeddings$embed(sentence) -->

<!-- # Step 3: Extract and store embeddings for each token -->
<!-- stacked_subset <- process_embeddings(sentence, verbose = TRUE) -->

<!-- # Step 4: Compute transformation matrix -->

<!-- st_transform <- compute_transform( -->
<!--    x = toks_fcm,                -->
<!--    pre_trained = stacked_subset, -->
<!--    weighting = 'log'           -->
<!-- ) -->

<!-- # Step 5: Generate document embeddings matrix -->
<!-- immig_dem_st <- dem( -->
<!--    x = immig_dfm,               -->
<!--    pre_trained = stacked_subset, -->
<!--    transform = TRUE,           -->
<!--    transform_matrix = st_transform, -->
<!--    verbose = TRUE              -->
<!-- ) -->

<!-- # Step 6: Fit conText model for analysis -->
<!-- set.seed(2021L)                  -->
<!-- st_model <- conText(formula = immigration ~ party + gender,   -->
<!--                     data = toks_nostop_feats,                 -->
<!--                     pre_trained = stacked_subset,           -->
<!--                     transform = TRUE,                       -->
<!--                     transform_matrix = st_transform,        -->
<!--                     jackknife = TRUE,                       -->
<!--                     confidence_level = 0.95,              -->
<!--                     permute = TRUE,                       -->
<!--                     num_permutations = 100,                -->
<!--                     window = 6,                           -->
<!--                     case_insensitive = TRUE,               -->
<!--                     verbose = FALSE) -->
<!-- ``` -->

<!-- ### Document Embedding Matrix Construction with BERT -->

<!-- <div style="text-align: justify;"> -->
<!-- BERT embeddings provide powerful contextual representations through their bidirectional transformer architecture. These embeddings are good at understanding context from both directions within text, generating deep contextual representations through multiple transformer layers, and leveraging pre-training on large text corpora to achieve strong performance across NLP tasks.  The classic BERT base model generates 768-dimensional embeddings for each token, providing rich semantic representations. -->

<!-- </div> -->

<!-- By utilizing the Flair framework, we also can seamlessly integrate: -->

<!-- - Multiple BERT variants like RoBERTa and DistilBERT -->
<!-- - Cross-lingual models such as XLM-RoBERTa   -->
<!-- - Domain-adapted BERT models -->
<!-- - Any transformer model available on HuggingFace -->



<!-- ```{r} -->
<!-- # Initialize BERT base uncased model embeddings from HuggingFace -->
<!-- bert_embeddings <- TransformerWordEmbeddings('bert-base-uncased') -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # Step 1: Create a Flair Sentence object from the text -->
<!-- sentence <- Sentence(paste(rownames(cr_glove_subset), collapse = " ")) -->

<!-- # Step 2: Generate embeddings using BERT model from HugginFace -->
<!-- bert_embeddings$embed(sentence) -->

<!-- # Step 3: Extract and store embeddings for each token -->
<!-- bert_subset <- process_embeddings(sentence, verbose = TRUE) -->

<!-- # Step 4: Compute transformation matrix  -->
<!-- bt_transform <- compute_transform(x = toks_fcm,      -->
<!--                                   pre_trained = bert_subset, -->
<!--                                   weighting = 'log') -->

<!-- # Step 5: Generate document embeddings matrix -->
<!-- immig_dem_bt <- dem(x = immig_dfm, -->
<!--                     pre_trained = bert_subset, -->
<!--                     transform = TRUE,           -->
<!--                     transform_matrix = bt_transform, -->
<!--                     verbose = TRUE) -->

<!-- # Step 6: Fit conText model for analysis -->
<!-- set.seed(2021L)                  -->
<!-- bt_model <- conText(formula = immigration ~ party + gender,   -->
<!--                     data = toks_nostop_feats,                 -->
<!--                     pre_trained = bert_subset,           -->
<!--                     transform = TRUE,                       -->
<!--                     transform_matrix = bt_transform,        -->
<!--                     jackknife = TRUE,                       -->
<!--                     confidence_level = 0.95,              -->
<!--                     permute = TRUE,                       -->
<!--                     num_permutations = 100,                -->
<!--                     window = 6,                           -->
<!--                     case_insensitive = TRUE,               -->
<!--                     verbose = FALSE) -->
<!-- ``` -->

<!-- ### Comparision of Different Embedding Approaches -->

<!-- <div style="text-align: justify;"> -->

<!-- While this tutorial doesn't determine a definitive best approach, it's important to understand the key distinctions between word embedding methods. BERT, FastText, Flair Stacked Embeddings, and GloVe can be categorized into two groups: dynamic and static embeddings. -->

<!-- Dynamic embeddings, particularly BERT and Flair, adapt their word representations based on context using high-dimensional vector spaces (BERT uses 768 dimensions in its base model). BERT employs self-attention mechanisms and subword tokenization, while Flair uses character-level modeling. Both effectively handle out-of-vocabulary words through these mechanisms. -->

<!-- However, there is a notable difference between their case study and here. While they provide selected words, we directly extract individual word vectors from BERT and Flair (forward/backward) embeddings using the same set of words. This doesn't truly utilize BERT and Flair embeddings' capability of modeling context. A more meaningful approach would be to extract embeddings at the quasi-sentence or paragraph level, or alternatively, to pool the entire document before extracting embeddings. -->

<!-- These context-based approaches stand in stark contrast to GloVe's methodology, which relies on pre-computed global word-word co-occurrence statistics to generate static word vectors. -->

<!-- </div> -->


<!-- ```{r echo=FALSE, message = TRUE, warning = TRUE, out.width="95%"} -->

<!-- st <- as.data.frame(st_model@normed_coefficients) -->
<!-- st["model"] <- "Flair Stacked Embeddings" -->
<!-- ft <- as.data.frame(ft_model@normed_coefficients) -->
<!-- ft["model"] <- "FastTest" -->
<!-- bt <- as.data.frame(bt_model@normed_coefficients) -->
<!-- bt["model"] <- "BERT" -->
<!-- ac <- as.data.frame(alc_model@normed_coefficients) -->
<!-- ac["model"] <- "Glove" -->

<!-- merged_df <- rbind(st,ft,bt,ac) -->

<!-- library(ggplot2) -->
<!-- # Create a faceted plot comparing different embedding results in a 2x2 grid -->
<!-- ggplot(merged_df, aes(x = coefficient, y = normed.estimate)) + -->
<!--  geom_errorbar(aes(ymin = lower.ci, ymax = upper.ci), width = 0.2) + -->
<!--  geom_point(size = 3) + -->
<!--  # Add reference line at y=0 -->
<!--  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") + -->
<!--  theme_minimal() + -->
<!--  labs( -->
<!--    title = "Estimated Coefficients with 95% CIs", -->
<!--    x = "", -->
<!--    y = "Normalized Estimate" -->
<!--  ) + -->
<!--  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + -->
<!--  facet_wrap(~model, nrow = 2, ncol = 2, scales = "free_y") -->
<!-- ``` -->

<!-- &nbsp; -->

-----

# Cite

```
@Manual{,
  title = {Flair NLP and flaiR for Social Science},
  author = {Yen-Chieh Liao},
  year = {2025},
  url = {https://davidycliao.github.io/flaiR/articles/tutorial.html}
}
```



